---
title: "clean_integration"
author: "T Attenborough"
date: "09/01/2023"
output: html_document
---

```{r}
library(Seurat) #Seurat v4.0.2
library(dplyr)
library(patchwork)
library(here)
library(ggplot2)
library(clustree)
library(SingleCellExperiment)
library(scater)
library(DoubletFinder)
library(zellkonverter)
library(basilisk)

#sessionInfo()
```

```{r}
run1.combined.v10 <- readRDS(file = "/Users/ta13/R_git/filtered_v10_miracidia/run1.combined.v10_integrated_55.rds")
```

```{r}
st=format(Sys.time(), "%Y-%m-%d") 
st
```

Import annotation information
```{r}
v9_genelist <- read.csv("/Users/ta13/R_git/r_teaching/WBPS17_genelist.csv", stringsAsFactors = FALSE, header = TRUE) #import the marker data from somule papaer
v9_genelist$X <- NULL 
```

First, I will import the R objects containing the filtered sorted and unsorted cells
```{r}
run1.sample1.sorted.filt <- readRDS(file = "/Users/ta13/R_git/filtered_v10_miracidia/run1.v10.sample1.sorted.filt.rds")

run1.sample2.unsorted.filt <- readRDS(file = "/Users/ta13/R_git/filtered_v10_miracidia/run1.v10.sample2.unsorted.filt_52.rds")

run1.sample3.unsorted.filt <- readRDS(file = "/Users/ta13/R_git/filtered_v10_miracidia/run1.v10.sample3.unsorted.filt_52.rds")

run1.sample4.sorted.filt <- readRDS(file = "/Users/ta13/R_git/filtered_v10_miracidia/run1.v10.sample4.sorted.filt.rds")
```

```{r}
run1.sorted.filt <- merge(run1.sample1.sorted.filt, y = run1.sample4.sorted.filt, add.cell.ids = c("sample1", "sample4"), project = "mira_sorted")

run1.unsorted.filt <- merge(run1.sample2.unsorted.filt, y = run1.sample3.unsorted.filt, add.cell.ids = c("sample2", "sample3"), project = "mira_unsorted")

run1.sorted.filt <- SCTransform(run1.sorted.filt, vars.to.regress = c("percent.mt", "plex"), verbose = FALSE, return.only.var.genes = FALSE)

run1.unsorted.filt <- SCTransform(run1.unsorted.filt, vars.to.regress = c("percent.mt", "plex"), verbose = FALSE, return.only.var.genes = FALSE)
```

Find variable features
```{r}
type_list <- c(run1.sorted.filt, run1.unsorted.filt)
# select features that are repeatedly variable across datasets for integration
features <- SelectIntegrationFeatures(object.list = type_list, nfeatures = 3000)
type_list <- PrepSCTIntegration(object.list = type_list, anchor.features = features)
```

Identify anchors and integrate
```{r}
run1.anchors <- FindIntegrationAnchors(object.list = type_list, anchor.features = features, normalization.method = "SCT")
# this command creates an 'integrated' data assay
run1.combined.v10 <- IntegrateData(anchorset = run1.anchors, normalization.method = "SCT")
```

Remove individual seurat objects not needed anyome
```{r}
# remove all objects that will not be used.
rm(run1.sample1.sorted.filt)
rm(run1.sample2.unsorted.filt)
rm(run1.sample3.unsorted.filt)
rm(run1.sample4.sorted.filt)

rm(run1.sorted.filt)
rm(run1.unsorted.filt)

rm(type_list)
rm(run1.anchors)
# run garbage collect to free up memory
gc()
```

```{r}
#Check how many PCs to use for the data using Mathews Molecular cross validation
source("/Users/ta13/R_tutorials/sporocysts/code.R")
mcv = molecularCrossValidation(run1.combined.v10@assays$RNA@counts, varGenes = VariableFeatures(run1.combined.v10),normalisation = minimalSeuratV3)

plotMCV(mcv)
```
Min PCs 25



```{r}
# specify that we will perform downstream analysis on the integrated data note that the
# original unmodified data still resides in the 'RNA' assay
DefaultAssay(run1.combined.v10) <- "integrated"

# Run the standard workflow for visualization and clustering
run1.combined.v10 <- RunPCA(run1.combined.v10, npcs = 100, verbose = FALSE)
ElbowPlot(run1.combined.v10, ndims = 100)  #ranks PCs by percentage of variation. A clear dropoff is sometimes seen, though not really here.
ggsave("run1.combined.v10.integrated.elbow.pdf")

run1.combined.v10 <- RunUMAP(run1.combined.v10, reduction = "pca", dims = 1:55)
run1.combined.v10 <- FindNeighbors(run1.combined.v10, reduction = "pca", dims = 1:55)
run1.combined.v10 <- FindClusters(run1.combined.v10, resolution = 0.5)

# Select a range of resolutions
resolution.range <- seq(from = 0, to = 1.5, by = 0.1)

# Find clusters using a range of resolutions
run1.combined.v10 <- Seurat::FindClusters(object = run1.combined.v10, resolution = resolution.range)

clustree(run1.combined.v10)
ggsave("run1.combined.v10.clust_55PC_0_to_1.5_tree_inte_52_plex.pdf",  width = 25, height = 15, units = c('cm'))
```

```{r}
run1.combined.v10 <- RunUMAP(run1.combined.v10, reduction = "pca", dims = 1:55)
run1.combined.v10 <- FindNeighbors(run1.combined.v10, reduction = "pca", dims = 1:55)
p2 <- DimPlot(run1.combined.v10, reduction = "umap", group.by = "plex", repel = TRUE, shuffle = TRUE)
p2
ggsave("filtered_PCs/run1clust-55-PC_integrate_52_plex.pdf", width = 25, height = 15, units = c('cm'))

run1.combined.v10 <- FindClusters(run1.combined.v10, resolution = 1)
p2 <- DimPlot(run1.combined.v10, reduction = "umap", label = TRUE, repel = TRUE)
p2
ggsave("filtered_PCs/run1clust-55-PC-1-res_integrate_52_clean.pdf")

plot1 <- FeaturePlot(run1.combined.v10, features = "Smp-071050")
LabelClusters(plot1, id = "ident", color = 'black', size =4, repel = T,  box.padding = 1.75, max.overlaps = Inf)
```

```{r}
DefaultAssay(run1.combined.v10) <- "integrated"

run1.combined.v10 <- FindClusters(run1.combined.v10, resolution = 2)

p2 <- DimPlot(run1.combined.v10, reduction = "umap", label = TRUE, repel = TRUE)
p2
ggsave("filtered_PCs/run1clust-55-PC-2-res_integrate_52_clean.pdf")
DefaultAssay(run1.combined.v10) <- "RNA"

VlnPlot(run1.combined.v10, features = "Smp-071050")
DefaultAssay(run1.combined.v10) <- "integrated"

run1.combined.v10 <- FindClusters(run1.combined.v10, resolution = 3)
p2 <- DimPlot(run1.combined.v10, reduction = "umap", label = TRUE, repel = TRUE)
p2
ggsave("filtered_PCs/run1clust-55-PC-3-res_integrate_52_clean.pdf")

DefaultAssay(run1.combined.v10) <- "RNA"

VlnPlot(run1.combined.v10, features = "Smp-071050")
DefaultAssay(run1.combined.v10) <- "integrated"

```

Cluster 36 gives the neuron 6 cluster

Print the cell IDs of the cluster 36 cells
```{r}
Idents(object = run1.combined.v10)
WhichCells(object = run1.combined.v10, ident = '36')
neuron6IDs <- WhichCells(object = run1.combined.v10, ident = '36')
```

Re-run the clustering at 1 res
```{r}
run1.combined.v10 <- FindNeighbors(run1.combined.v10, dims = 1:55)
run1.combined.v10 <- FindClusters(run1.combined.v10, resolution = 1,  algorithm = 1)
run1.combined.v10 <- RunUMAP(run1.combined.v10, dims = 1:55)
DimPlot(run1.combined.v10, reduction = "umap", label = TRUE)+ NoLegend()
ggsave("run1.combined.v10_pc55_res1.pdf", width = 15, height = 15, units = c('cm'))

```

How many clusters?
```{r}
table(Idents(run1.combined.v10))
```

Rename the neuron 6 cluster as 5

```{r}
Idents(run1.combined.v10, cells = c(neuron6IDs)) <- '18'
head(Idents(run1.combined.v10))
table(Idents(run1.combined.v10))
```

PLot the UMAP
```{r}
DimPlot(run1.combined.v10, reduction = "umap", label = TRUE)+ NoLegend()
```

```{r}
FeaturePlot(run1.combined.v10, features="percent.mt", label=TRUE)
ggsave("run1.combined.v10_55PC_1res_mt_SCT_52_plex.pdf")

FeaturePlot(run1.combined.v10, features="nCount_RNA", label=TRUE)
ggsave("run1.combined.v10_55PC_1res_UMIs_SCT_52_plex.pdf")

FeaturePlot(run1.combined.v10, features="nFeature_RNA", label=TRUE)
ggsave("run1.combined.v10_55PC_1res_genes_SCT_52_plex.pdf")
```
Find all markers
```{r}
DefaultAssay(run1.combined.v10) <- "SCT"
run1.combined.v10 <- SCTransform(run1.combined.v10, vars.to.regress = c("percent.mt", "plex"), verbose = FALSE, return.only.var.genes = FALSE)

PrepSCTFindMarkers(run1.combined.v10, assay = "SCT", verbose = TRUE)

#find all markers
run1.combined.v10.markers_roc_no_lbls <- FindAllMarkers(run1.combined.v10, only.pos = TRUE, min.pct = 0.0, logfc.threshold = 0.0, test.use = "roc", return.thresh = 0)

run1.combined.v10.top5_roc_no_lbls=run1.combined.v10.markers_roc_no_lbls %>% group_by(cluster) %>% top_n(n = 5, wt = myAUC)# groups the markers by cluster, then picks the top 5 most differentiually expressed markers
write.csv(x=run1.combined.v10.markers_roc_no_lbls, file="top5_markerz_roc_no_lbls_run1.combined.v10_jan23.csv")
write.csv(x=run1.combined.v10.markers_roc_no_lbls, file="markerz_roc_no_lbls_run1.combined.v10_jan23.csv")

```

Plot top 5 markers of each cluster by AUC
```{r}
run1.combined.v10.markers_roc_no_lbls$gene <- gsub('\\_', '-', run1.combined.v10.markers_roc_no_lbls$gene) #replace dashes in geneid with underscores
dotplot_features=run1.combined.v10.markers_roc_no_lbls %>% group_by(cluster) %>% top_n(n = 5, wt = myAUC)

DotPlot(object = run1.combined.v10, features = unique(dotplot_features$gene)) + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+ scale_color_viridis(discrete = FALSE)
ggsave("run1.combined.v10_top5genes_roc_nolbl_jul5.pdf", width = 35, height = 15, units = c('cm'))

dotplot_features=run1.combined.v10.markers_roc_no_lbls %>% group_by(cluster) %>% top_n(n = 3, wt = myAUC)

DotPlot(object = run1.combined.v10, features = unique(dotplot_features$gene)) + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+ scale_color_viridis(discrete = FALSE)
ggsave("run1.combined.v10_top3genes_roc_nolbl_jul5.pdf", width = 30, height = 15, units = c('cm'))

```

```{r}
saveRDS(run1.combined.v10, file = "run1.combined.v10_integrated_55.rds") #saves this version of the dataset


```



```{r}
DefaultAssay(run1.combined.v10) <- "integrated"
run1.combined.v10 <- RenameIdents(object = run1.combined.v10, 
                               "0" = "Muscle 1",
                               "1" = "Stem C",
                               "2" = "Stem D",
                               "3" = "Stem F",
                               "4" = "Stem A",
                               "5" = "Stem B",
                               "6" = "Neuron 1",
                               "7" = "Muscle 2",
                               "8" = "Neuron 2",
                               "9" = "Parenchyma 1",
                               "10" = "Stem E",
                               "11" = "Parenchyma 2",
                               "12" = "Protonephridia",
                               "13" = "Tegument",
                               "14" = "Neuron 3",
                               "15" = "Neuron 5",
                               "16" = "Stem G",
                               "17" = "Neuron 4", 
                              "18" = "Neuron 6")


run1.combined.v10[["merge.ident"]] <- Idents(object = run1.combined.v10)
run1.combined.v10[["may.ident"]] <- Idents(object = run1.combined.v10)

DimPlot(run1.combined.v10, reduction = "umap", label=TRUE) #visulaises the UMAP
p2 <- DimPlot(run1.combined.v10, reduction = "umap", label = TRUE, repel = TRUE)
p2

ggsave("run1.combined.v10_55PC_1res_lbl.pdf")
```

```{r}
DefaultAssay(run1.combined.v10) <- "SCT"
run1.combined.v10 <- SCTransform(run1.combined.v10, vars.to.regress = c("percent.mt", "plex"), verbose = FALSE, return.only.var.genes = FALSE)

PrepSCTFindMarkers(run1.combined.v10, assay = "SCT", verbose = TRUE)

#find all markers
run1.combined.v10.markers_roc_with_lbls <- FindAllMarkers(run1.combined.v10, only.pos = TRUE, min.pct = 0.0, logfc.threshold = 0.0, test.use = "roc", return.thresh = 0)

run1.combined.v10.top5_roc_with_lbls=run1.combined.v10.markers_roc_with_lbls %>% group_by(cluster) %>% top_n(n = 5, wt = myAUC)# groups the markers by cluster, then picks the top 5 most differentiually expressed markers
write.csv(x=run1.combined.v10.top5_roc_with_lbls, file="top5_markerz_roc_with_lbls_run1.combined.v10_jan23.csv")
write.csv(x=run1.combined.v10.markers_roc_with_lbls, file="markerz_roc_with_lbls_run1.combined.v10_jan23.csv")
```

Add the annotations from v9 to the genelist
```{r}
run1.combined.v10.markers_roc_with_lbls$gene <- gsub('\\-', '_', run1.combined.v10.markers_roc_with_lbls$gene) #replace dashes in geneid with underscores

run1.combined.v10.markers_roc_with_lbls <- run1.combined.v10.markers_roc_with_lbls %>% left_join(v9_genelist, by = c("gene" = "Name")) #check the top 5 marker genes are also in the somule paper
write.csv(x=run1.combined.v10.markers_roc_with_lbls, file=paste0('markerz_roc_with_lbls_run1.combined.v10_annotate_', st, '.csv')) #save this as a csv
```

Add the annotations from v9 to the genelist
```{r}
run1.combined.v10.top5_roc_with_lbls$gene <- gsub('\\-', '_', run1.combined.v10.top5_roc_with_lbls$gene) #replace dashes in geneid with underscores

run1.combined.v10.top5_roc_with_lbls <- run1.combined.v10.top5_roc_with_lbls %>% left_join(v9_genelist, by = c("gene" = "Name")) #check the top 5 marker genes are also in the somule paper
write.csv(x=run1.combined.v10.top5_roc_with_lbls, file=paste0('top5_markerz_roc_with_lbls_run1.combined.v10_annotate_', st, '.csv')) #save this as a csv
```

Plot top 5 markers of each cluster by AUC
```{r}
run1.combined.v10.markers_roc_with_lbls$gene <- gsub('\\_', '-', run1.combined.v10.markers_roc_with_lbls$gene) #replace dashes in geneid with underscores
dotplot_features=run1.combined.v10.markers_roc_with_lbls %>% group_by(cluster) %>% top_n(n = 5, wt = myAUC)

DotPlot(object = run1.combined.v10, features = unique(dotplot_features$gene)) + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+ scale_color_viridis(discrete = FALSE)
ggsave("run1.combined.v10_top5genes_roc_withlbl_jul5.pdf", width = 35, height = 15, units = c('cm'))

dotplot_features=run1.combined.v10.markers_roc_with_lbls %>% group_by(cluster) %>% top_n(n = 3, wt = myAUC)

DotPlot(object = run1.combined.v10, features = unique(dotplot_features$gene)) + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+ scale_color_viridis(discrete = FALSE)
ggsave("run1.combined.v10_top3genes_roc_withlbl_jul5.pdf", width = 30, height = 15, units = c('cm'))
```


```{r}
plot1 <- FeaturePlot(run1.combined.v10, features = "Smp-071050")
LabelClusters(plot1, id = "ident", color = 'black', size =4, repel = T,  box.padding = 1.75, max.overlaps = Inf)
```

Make a new color pallete for the 'fancy' umap
```{r}
new_pal <- c("#c4b7cb","#007aaa","#ffb703","#c40c18","#fb8500","#7851a9","#00325b","#8ACB88","#107E7D", "#FB6376", "#57467B", "#FFFD82", "#2191FB", "#690500", "#B3E9C7", "#B57F50","#2C514C","#754043" ,"#69A297" )
scales::show_col(new_pal)
plot1 <- DimPlot(run1.combined.v10, reduction = "umap", label = FALSE, repel = TRUE, label.box = FALSE) + NoLegend() +scale_color_manual(values = new_pal)
LabelClusters(plot1, id = "ident", color = 'black', size =4, repel = T,  box.padding = 1.75)

ggsave("run1.combined.v10_umap_fancylabels_jan23.pdf", width = 25, height = 20, units = c('cm'))
ggsave("run1.combined.v10_umap_fancylabels_jan23_small.pdf")
```


