---
title: "figs_for_update"
author: "T Attenborough"
date: "2024-05-07"
output: html_document
---

```{r}
library(Seurat) #Seurat v4.0.2
library(dplyr)
library(patchwork)
library(here)
library(ggplot2)
library(clustree)
library(SingleCellExperiment)
library(scater)
library(DoubletFinder)
library(zellkonverter)
library(basilisk)
library(ggpubr)

#sessionInfo()
```

```{r}
run1.combined.v10 <- readRDS(file = "/Users/ta13/R_git/filtered_v10_miracidia/run1.combined.v10_integrated_55.rds")
```

```{r}
st=format(Sys.time(), "%Y-%m-%d") 
st
```

```{r}
DefaultAssay(run1.combined.v10) <- "integrated"
run1.combined.v10 <- RenameIdents(object = run1.combined.v10, 
                               "0" = "Muscle 1",
                               "1" = "Stem C",
                               "2" = "Stem D",
                               "3" = "Stem F",
                               "4" = "Stem A",
                               "5" = "Stem B",
                               "6" = "Neuron 1",
                               "7" = "Muscle 2",
                               "8" = "Neuron 4",
                               "9" = "Parenchyma 1",
                               "10" = "Stem E",
                               "11" = "Parenchyma 2",
                               "12" = "Protonephridia",
                               "13" = "Tegument",
                               "14" = "Neuron 2",
                               "15" = "Neuron 5",
                               "16" = "Stem G",
                               "17" = "Ciliary plate", 
                              "18" = "Neuron 3")


run1.combined.v10[["merge.ident"]] <- Idents(object = run1.combined.v10)
run1.combined.v10[["may.ident"]] <- Idents(object = run1.combined.v10)

DimPlot(run1.combined.v10, reduction = "umap", label=TRUE) #visulaises the UMAP
p2 <- DimPlot(run1.combined.v10, reduction = "umap", label = TRUE, repel = TRUE)
p2
```

Import annotation information
```{r}
v10_genelist <- read.csv("/Users/ta13/R_git/cerc_som_v10/v10_genes_with_descriptions_2023-04-17.csv", stringsAsFactors = FALSE, header = TRUE) #import the marker data from cercule papaer
v10_genelist$X <- NULL 
```

Make a new color pallete for the 'fancy' umap
```{r}
new_pal <- c("#9E0059","#007aaa","#ffb703","#B3E9C7","#fb8500","#7851a9","#00325b","#8ACB88","#107E7D", "#FB6376", "#c40c18", "#FFFD82", "#2191FB", "#690500", "#57467B", "#B57F50","#2C514C","#c4b7cb" ,"#FFCDB2" )
scales::show_col(new_pal)
plot1 <- DimPlot(run1.combined.v10, reduction = "umap", label = FALSE, repel = TRUE, label.box = FALSE) + NoLegend() +scale_color_manual(values = new_pal)
LabelClusters(plot1, id = "ident", color = 'black', size =4, repel = T,  box.padding = 1.75)

ggsave(paste("figs_may24/run1.combined.v10_umap_oldfancylabels-",st, ".pdf", sep = ""), width = 25, height = 20, units = c('cm'))
ggsave(paste("figs_may24/run1.combined.v10_umap_oldfancylabels-small-",st, ".pdf", sep = ""))
```


##Show sorted/unsorted
```{r}
plot1 <- DimPlot(run1.combined.v10, reduction = "umap", label = FALSE, repel = TRUE, label.box = FALSE, split.by = "type") + NoLegend() +scale_color_manual(values = new_pal)
plot2 <- LabelClusters(plot1, id = "ident", color = 'black', size =4, repel = T,  box.padding = 1.75, max.overlaps = Inf)
plot2

my_pal <- c("#BA2D0B", "#8EB1C7")
plot3 <- DimPlot(run1.combined.v10, reduction = "umap", label = FALSE, repel = TRUE, group.by = "type", shuffle = TRUE)+scale_color_manual(values = my_pal)
plot3
ggsave(paste("figs_may24/run1.combined.v10_umap_sorting-small-",st, ".pdf", sep = ""))


my_pal <- c("#DF9A57", "#306B34", "#EDADC7", "#2A628F")
plot4 <- DimPlot(run1.combined.v10, reduction = "umap", label = FALSE, repel = TRUE, group.by = "plex", shuffle = TRUE)+scale_color_manual(values = my_pal)
plot4
ggsave(paste("figs_may24/run1.combined.v10_umap_sample-small-",st, ".pdf", sep = ""))


plot2 /
  (plot3 + plot4) +  plot_layout(guides = "collect")
ggsave(paste("figs_may24/run1.combined.v10_umap_sorting-patchwork-",st, ".pdf", sep = ""), width = 30, height = 20, units = c('cm'))

```
Subcluster stem F and G?

```{r}

```

Ago in all cells
```{r}
DefaultAssay(run1.combined.v10) <- "RNA"
plot1 <- FeaturePlot(run1.combined.v10, features = "Smp-179320")
LabelClusters(plot1, id = "ident", color = 'black', size =4, repel = T,  box.padding = 1.75, max.overlaps = Inf)
ggsave("figs_may24/run1.combined.v10-umap-Smp-179320-.pdf", width = 25, height = 15, units = c('cm'))
```

Co-expression of ago and complexin
```{r}
DefaultAssay(run1.combined.v10) <- "RNA"

coexpression.plot <-FeaturePlot(run1.combined.v10, features = c("Smp-179320", "Smp-050220"), blend = TRUE)
coexpression.plot
ggsave(paste("figs_may24/run1.combined.v10-coexpressed-Smp-179320-Smp-050220.pdf"), width = 50, height = 20, units = c('cm'))
```

```{r}
library(scCustomize)
run1.combined.v10 <- subset(x = run1.combined.v10, idents = c("Stem F"))

percent <- scCustomize::Percent_Expressing(seurat_object = run1.combined.v10, features = c("Smp-050220"))
```

Plot the 5 neurogenins from WBPS
```{r}
DefaultAssay(run1.combined.v10) <- "RNA"
plot1 <- FeaturePlot(run1.combined.v10, features = "Smp-125400")
LabelClusters(plot1, id = "ident", color = 'black', size =4, repel = T,  box.padding = 1.75, max.overlaps = Inf)
ggsave("figs_may24/run1.combined.v10-umap-Smp-125400-.pdf", width = 25, height = 15, units = c('cm'))

plot1 <- FeaturePlot(run1.combined.v10, features = "Smp-082290")
LabelClusters(plot1, id = "ident", color = 'black', size =4, repel = T,  box.padding = 1.75, max.overlaps = Inf)
ggsave("figs_may24/run1.combined.v10-umap-Smp-082290-.pdf", width = 25, height = 15, units = c('cm'))

plot1 <- FeaturePlot(run1.combined.v10, features = "Smp-067430")
LabelClusters(plot1, id = "ident", color = 'black', size =4, repel = T,  box.padding = 1.75, max.overlaps = Inf)
ggsave("figs_may24/run1.combined.v10-umap-Smp-067430-.pdf", width = 25, height = 15, units = c('cm'))

plot1 <- FeaturePlot(run1.combined.v10, features = "Smp-072470")
LabelClusters(plot1, id = "ident", color = 'black', size =4, repel = T,  box.padding = 1.75, max.overlaps = Inf)
ggsave("figs_may24/run1.combined.v10-umap-Smp-072470-.pdf", width = 25, height = 15, units = c('cm'))

plot1 <- FeaturePlot(run1.combined.v10, features = "Smp-000620")
LabelClusters(plot1, id = "ident", color = 'black', size =4, repel = T,  box.padding = 1.75, max.overlaps = Inf)
ggsave("figs_may24/run1.combined.v10-umap-Smp-000620-.pdf", width = 25, height = 15, units = c('cm'))
```

What percentage of cells come from each method?
```{r}
table(run1.combined.v10$may.ident)

run1.combined.v10 <- subset(x = run1.combined.v10, subset = type == "sorted")
table(run1.combined.v10$may.ident)

run1.combined.v10 <- subset(x = run1.combined.v10, subset = type == "unsorted")
table(run1.combined.v10$may.ident)
```

Subcluster neuron 1

```{r}
run1.combined.v10 <- subset(x = run1.combined.v10, idents = c("Neuron 1"))

DefaultAssay(run1.combined.v10) <- "RNA"

run1.combined.v10 <- NormalizeData(run1.combined.v10)
run1.combined.v10 <- FindVariableFeatures(run1.combined.v10, selection.method = "vst", nfeatures = 2000)
# Identify the 10 most highly variable genes
top10 <- head(VariableFeatures(run1.combined.v10), 10)
top10

all.genes <- rownames(run1.combined.v10)
run1.combined.v10 <- ScaleData(run1.combined.v10, features = all.genes)
run1.combined.v10 <- RunPCA(run1.combined.v10, features = VariableFeatures(object = run1.combined.v10),npcs = 100) #shows top contributing features for the PCs
VizDimLoadings(run1.combined.v10, dims = 1:2, reduction = "pca") #shows the weightings of top contributing features to pcs 1 and 2
DimHeatmap(run1.combined.v10, dims = 1, cells = 500, balanced = TRUE) #plots heatmap of top 500 mist variable cells for PC1, with relative gene expression
DimHeatmap(run1.combined.v10, dims = 1:15, cells = 500, balanced = TRUE) #this gives the heatmaps for PCs 1-15, so you can visually inspect the genes/PCs
DefaultAssay(run1.combined.v10) <- "RNA"
ElbowPlot(run1.combined.v10, ndims = 100)  #ranks PCs by percentage of variation. A clear dropoff is sometimes seen, though not really here.
ggsave("figs_may24/run1.combined.v10_elbowplot100_RNA.pdf")

run1.combined.v10 <- FindNeighbors(run1.combined.v10, dims = 1:25) #here construct k-nearst neighbours graoh based on euclidean distance in PCA space, then refine edge weights based on Jaccard similarity. this takes the number of PCs previously determined as importan (here 15 PCs_)
run1.combined.v10 <- FindClusters(run1.combined.v10, resolution = 0.2) #this iteratively groups cells using Louvain algorithm (default). Resolution sets the granularity. 0.4-1.2 gives good results for ~3K cells, with larger number suiting larger datasets.
run1.combined.v10 <- RunUMAP(run1.combined.v10, dims = 1:25) #runs umap to visualise the clusters. Need to set the number of PCs
DimPlot(run1.combined.v10, reduction = "umap", label=T) #visulaises the UMAP
ggsave("figs_may24/run1.combined.v10clust_25PC_0.2res_RNA26PC_only_neuron_1.pdf")

run1.combined.v10 <- SCTransform(run1.combined.v10, verbose = TRUE)
#DefaultAssay(run1.combined.v10) <- "SCT"
run1.combined.v10 <- RunPCA(run1.combined.v10, features = VariableFeatures(object = run1.combined.v10), npcs=100) #shows top contributing features for the PCs
VizDimLoadings(run1.combined.v10, dims = 1:2, reduction = "pca") #shows the weightings of top contributing features to pcs 1 and 2
DimHeatmap(run1.combined.v10, dims = 1, cells = 500, balanced = TRUE) #plots heatmap of top 500 mist variable cells for PC1, with relative gene expression
ElbowPlot(run1.combined.v10, ndims = 100)  #ranks PCs by percentage of variation. A clear dropoff is sometimes seen, though not really here.
ggsave("figs_may24/run1.combined.v10_elbowplot100_SCT.pdf")

run1.combined.v10 <- FindNeighbors(run1.combined.v10, dims = 1:19) #here construct k-nearst neighbours graoh based on euclidean distance in PCA space, then refine edge weights based on Jaccard similarity. this takes the number of PCs previously determined as importan (here 15 PCs_)
run1.combined.v10 <- FindClusters(run1.combined.v10, resolution = 0.3) #this iteratively groups cells using Louvain algorithm (default). Resolution sets the granularity. 0.4-1.2 gives good results for ~3K cells, with larger number suiting larger datasets.
run1.combined.v10 <- RunUMAP(run1.combined.v10, dims = 1:19) #runs umap to visualise the clusters. Need to set the number of PCs
DimPlot(run1.combined.v10, reduction = "umap") #visulaises the UMAP
ggsave("figs_may24/run1.combined.v10clust_19PC_0.3res_SCT.pdf", width = 25, height = 15, units = c('cm'))

plot1 <- FeaturePlot(run1.combined.v10, features = "Smp-332250")
LabelClusters(plot1, id = "ident", color = 'black', size =4, repel = T,  box.padding = 1.75, max.overlaps = Inf)
ggsave("figs_may24/run1.combined.v10-neuron1-umap-Smp-332250-.pdf", width = 25, height = 15, units = c('cm'))
```

How many cells express the neurogenins?
```{r}
library(scCustomize)
percent <- scCustomize::Percent_Expressing(seurat_object = run1.combined.v10, features = c("Smp-072470"))
```

Co-expression of nanos and fgfrA
```{r}
DefaultAssay(run1.combined.v10) <- "RNA"

coexpression.plot <-FeaturePlot(run1.combined.v10, features = c("Smp-051920", "Smp-175590"), blend = TRUE)
coexpression.plot
ggsave(paste("figs_may24/run1.combined.v10-coexpressed-Smp-051920-Smp-175590.pdf"), width = 50, height = 20, units = c('cm'))
```

Co-expression of nanos and fgfrA
```{r}
DefaultAssay(run1.combined.v10) <- "RNA"

coexpression.plot <-FeaturePlot(run1.combined.v10, features = c("Smp-051920", "Smp-024860"), blend = TRUE)
coexpression.plot
ggsave(paste("figs_may24/run1.combined.v10-coexpressed-Smp-051920-Smp-024860.pdf"), width = 50, height = 20, units = c('cm'))
```