---
title: "go_analysis_miracidia"
author: "T Attenborough"
date: "2023-10-12"
output: html_document
---

```{r}
library(Seurat) #Seurat v4.0.2
library(dplyr)
library(patchwork)
library(here)
library(ggplot2)
library(clustree)
library(SingleCellExperiment)
library(scater)
library(zellkonverter)
library(basilisk)
library(RColorBrewer)
library(dittoSeq)
library(biomaRt) #initialise biomaRt
library(rtracklayer) #initialise biomaRt
library(hues)
library(rstatix)
library(cowplot)
library(magick)
library(tidyverse)
library(forcats)
library(topGO)
library(data.table)
#sessionInfo()
```

```{r}
run1.combined.v10 <- readRDS(file = "/Users/ta13/R_git/filtered_v10_miracidia/run1.combined.v10_integrated_55.rds")

DefaultAssay(run1.combined.v10) <- "RNA"
```

```{r}
st=format(Sys.time(), "%Y-%m-%d") 
st
```

Import go term file from WBPS biomart
```{r}
myGO <- read.delim("/Users/ta13/R_git/GOterms_v10_fromWBPS18.txt", header = TRUE, sep = "\t", dec = ".")
```

Remove the col with genome ID: this is the same in every row
```{r}
myGO$Genome.project <- NULL
```

Collapse the columns by 
```{r}
myGO_squish = as.data.table(myGO)
myGO_squish = myGO_squish[, lapply(.SD, paste0, collapse=","), by=Gene.stable.ID]
myGO_squish = as.data.frame(myGO_squish)
```

```{r}
write.table(myGO_squish, "/Users/ta13/R_git/GOterm_dict_WBPS18.txt", append = FALSE, sep = " ", dec = ".",
            row.names = FALSE, col.names = FALSE)
```


Make a GO term dictionary from gene:GO mappings
```{r}
geneID2GO <- readMappings(file = "/Users/ta13/R_git/GOterm_dict_WBPS18.txt", sep = " ") 
```

```{r}
geneUniverse <- names(geneID2GO) 
```

Only want to include genes in the gene universe that were detected in the dataset.
Extract a list of all genes for comparison
```{r}
allGenesInMira <- rownames(x = run1.combined.v10)

head(allGenesInMira)

allGenesInMira <- data.frame(allGenesInMira)
allGenesInMira$allGenesInMira <- gsub('\\-', '_', allGenesInMira$allGenesInMira) #replace dashes with underscores
write.csv(x=allGenesInMira, file="allGenesInMira.csv") #save this as a csv
```

So here, I will use only the genes detected in the miracidia data as the gene universe. topGO doc says that: "The set of all genes from the array/study will be referred from now on as the gene universe."

Import the list of genes in the mira dataset
```{r}
listOfMiraGenes <- read.csv("/Users/ta13/R_git/v10_miracidia/allGenesInMira.csv", header=TRUE, stringsAsFactors=FALSE)
listOfMiraGenes$X <- NULL

listOfMiraGenes <- listOfMiraGenes$allGenesInMira
```

Find the common elements from the full gene list from schisto, and the genes detected in miracidia data
```{r}
miracidia_geneUniverse <- intersect(geneUniverse,listOfMiraGenes)
```
