---
title: "go_analysis_miracidia"
author: "T Attenborough"
date: "2023-10-12"
output: html_document
---

```{r}
library(Seurat) #Seurat v4.0.2
library(dplyr)
library(patchwork)
library(here)
library(ggplot2)
library(clustree)
library(SingleCellExperiment)
library(scater)
library(zellkonverter)
library(basilisk)
library(RColorBrewer)
library(dittoSeq)
library(biomaRt) #initialise biomaRt
library(rtracklayer) #initialise biomaRt
library(hues)
library(rstatix)
library(cowplot)
library(magick)
library(tidyverse)
library(forcats)
library(topGO)
library(data.table)
#sessionInfo()
```

```{r}
run1.combined.v10 <- readRDS(file = "/Users/ta13/R_git/filtered_v10_miracidia/run1.combined.v10_integrated_55.rds")

DefaultAssay(run1.combined.v10) <- "RNA"
```

```{r}
st=format(Sys.time(), "%Y-%m-%d") 
st
```

Import go term file from WBPS biomart
```{r}
myGO <- read.delim("/Users/ta13/R_git/GOterms_v10_fromWBPS18_justgenes.txt", header = TRUE, sep = "\t", dec = ".")
```

Remove the col with genome ID: this is the same in every row
```{r}
myGO$Genome.project <- NULL
```

Collapse the columns by 
```{r}
myGO_squish = as.data.table(myGO)
myGO_squish = myGO_squish[, lapply(.SD, paste0, collapse=","), by=Gene.stable.ID]
myGO_squish = as.data.frame(myGO_squish)
```

```{r}
write.table(myGO_squish, "/Users/ta13/R_git/GOterm_dict_WBPS18.txt", append = FALSE, sep = " ", dec = ".",
            row.names = FALSE, col.names = FALSE)
```


Make a GO term dictionary from gene:GO mappings
```{r}
geneID2GO <- readMappings(file = "/Users/ta13/R_git/GOterm_dict_WBPS18.txt", sep = " ") 
```

```{r}
geneUniverse <- names(geneID2GO) 
```

Only want to include genes in the gene universe that were detected in the dataset.
Extract a list of all genes for comparison
```{r}
allGenesInMira <- rownames(x = run1.combined.v10)

head(allGenesInMira)

allGenesInMira <- data.frame(allGenesInMira)
allGenesInMira$allGenesInMira <- gsub('\\-', '_', allGenesInMira$allGenesInMira) #replace dashes with underscores
write.table(x=allGenesInMira, file="v10_GO_genelists/allGenesInMira.csv", col.names=FALSE, row.names=FALSE)
```

So here, I will use only the genes detected in the miracidia data as the gene universe. topGO doc says that: "The set of all genes from the array/study will be referred from now on as the gene universe."

Import the list of genes in the mira dataset
```{r}
listOfMiraGenes <- read.csv("/Users/ta13/R_git/filtered_v10_miracidia/allGenesInMira.csv", header=TRUE, stringsAsFactors=FALSE)
listOfMiraGenes$X <- NULL

listOfMiraGenes <- listOfMiraGenes$allGenesInMira
```

Find the common elements from the full gene list from schisto, and the genes detected in miracidia data
```{r}
miracidia_geneUniverse <- intersect(myGO_squish$Gene.stable.ID,listOfMiraGenes)
head(miracidia_geneUniverse)
```

Next, generate the gene lists for each cluster (and tissue type). Start by importing the marker gene list.
```{r}
markerGeneList <- read.csv("/Users/ta13/R_git/filtered_v10_miracidia/markerz_roc_with_lbls_run1.combined.v10_annotate_2023-01-23.csv", header=TRUE, stringsAsFactors=FALSE)
```

```{r}
table(markerGeneList$cluster)
```



```{r}
clustX <- markerGeneList[grepl('Muscle 1',markerGeneList$cluster),]
#Select just those with at least myAUC of 0.7
clustX <- clustX %>%
  filter(myAUC >= 0.7)

clustX$gene <- gsub('\\-', '_', clustX$gene) #replace dashes in geneid with underscores
write.table(x=clustX$gene, file="v10_GO_genelists/Muscle-1_Markers_Oct12_justgenes.csv", col.names=FALSE, row.names=FALSE)
```

```{r}
clustX <- markerGeneList[grepl('Muscle 2',markerGeneList$cluster),]
#Select just those with at least myAUC of 0.7
clustX <- clustX %>%
  filter(myAUC >= 0.7)

clustX$gene <- gsub('\\-', '_', clustX$gene) #replace dashes in geneid with underscores
write.table(x=clustX$gene, file="v10_GO_genelists/Muscle-2_Markers_Oct12_justgenes.csv", col.names=FALSE, row.names=FALSE)
```

```{r}
clustX <- markerGeneList[grepl('Muscle 1',markerGeneList$cluster) | grepl('Muscle 2',markerGeneList$cluster),]
#Select just those with at least myAUC of 0.7
clustX <- clustX %>%
  filter(myAUC >= 0.7)

clustX$gene <- gsub('\\-', '_', clustX$gene) #replace dashes in geneid with underscores
table(clustX$gene)
clustX <- unique(clustX$gene)

write.table(x=clustX, file="v10_GO_genelists/Muscle-all_Markers_Oct12_justgenes.csv", col.names=FALSE, row.names=FALSE)
```

```{r}
clustX <- markerGeneList[grepl('Neuron 1',markerGeneList$cluster),]
#Select just those with at least myAUC of 0.7
clustX <- clustX %>%
  filter(myAUC >= 0.7)

clustX$gene <- gsub('\\-', '_', clustX$gene) #replace dashes in geneid with underscores
write.table(x=clustX$gene, file="v10_GO_genelists/Neuron-1_Markers_Oct12_justgenes.csv", col.names=FALSE, row.names=FALSE)
```

```{r}
clustX <- markerGeneList[grepl('Neuron 2',markerGeneList$cluster),]
#Select just those with at least myAUC of 0.7
clustX <- clustX %>%
  filter(myAUC >= 0.7)

clustX$gene <- gsub('\\-', '_', clustX$gene) #replace dashes in geneid with underscores
write.table(x=clustX$gene, file="v10_GO_genelists/Neuron-2_Markers_Oct12_justgenes.csv", col.names=FALSE, row.names=FALSE)
```

```{r}
clustX <- markerGeneList[grepl('Neuron 3',markerGeneList$cluster),]
#Select just those with at least myAUC of 0.7
clustX <- clustX %>%
  filter(myAUC >= 0.7)

clustX$gene <- gsub('\\-', '_', clustX$gene) #replace dashes in geneid with underscores
write.table(x=clustX$gene, file="v10_GO_genelists/Neuron-3_Markers_Oct12_justgenes.csv", col.names=FALSE, row.names=FALSE)
```

```{r}
clustX <- markerGeneList[grepl('Neuron 4',markerGeneList$cluster),]
#Select just those with at least myAUC of 0.7
clustX <- clustX %>%
  filter(myAUC >= 0.7)

clustX$gene <- gsub('\\-', '_', clustX$gene) #replace dashes in geneid with underscores
write.table(x=clustX$gene, file="v10_GO_genelists/Neuron-4_Markers_Oct12_justgenes.csv", col.names=FALSE, row.names=FALSE)
```

```{r}
clustX <- markerGeneList[grepl('Neuron 5',markerGeneList$cluster),]
#Select just those with at least myAUC of 0.7
clustX <- clustX %>%
  filter(myAUC >= 0.7)

clustX$gene <- gsub('\\-', '_', clustX$gene) #replace dashes in geneid with underscores
write.table(x=clustX$gene, file="v10_GO_genelists/Neuron-5_Markers_Oct12_justgenes.csv", col.names=FALSE, row.names=FALSE)
```

```{r}
clustX <- markerGeneList[grepl('Neuron 6',markerGeneList$cluster),]
#Select just those with at least myAUC of 0.7
clustX <- clustX %>%
  filter(myAUC >= 0.7)

clustX$gene <- gsub('\\-', '_', clustX$gene) #replace dashes in geneid with underscores
write.table(x=clustX$gene, file="v10_GO_genelists/Neuron-6_Markers_Oct12_justgenes.csv", col.names=FALSE, row.names=FALSE)
```

```{r}
clustX <- markerGeneList[grepl('Neuron 1',markerGeneList$cluster) | grepl('Neuron 2',markerGeneList$cluster) | grepl('Neuron 3',markerGeneList$cluster) | grepl('Neuron 5',markerGeneList$cluster) | grepl('Neuron 6',markerGeneList$cluster),]
#Select just those with at least myAUC of 0.7
clustX <- clustX %>%
  filter(myAUC >= 0.7)

clustX$gene <- gsub('\\-', '_', clustX$gene) #replace dashes in geneid with underscores
table(clustX$gene)
clustX <- unique(clustX$gene)

write.table(x=clustX, file="v10_GO_genelists/Neuron-all_Markers_Oct12_justgenes.csv", col.names=FALSE, row.names=FALSE)
```

```{r}
clustX <- markerGeneList[grepl('Parenchyma 1',markerGeneList$cluster),]
#Select just those with at least myAUC of 0.7
clustX <- clustX %>%
  filter(myAUC >= 0.7)

clustX$gene <- gsub('\\-', '_', clustX$gene) #replace dashes in geneid with underscores
write.table(x=clustX$gene, file="v10_GO_genelists/Parenchyma-1_Markers_Oct12_justgenes.csv", col.names=FALSE, row.names=FALSE)
```

```{r}
clustX <- markerGeneList[grepl('Parenchyma 2',markerGeneList$cluster),]
#Select just those with at least myAUC of 0.7
clustX <- clustX %>%
  filter(myAUC >= 0.7)

clustX$gene <- gsub('\\-', '_', clustX$gene) #replace dashes in geneid with underscores
write.table(x=clustX$gene, file="v10_GO_genelists/Parenchyma-2_Markers_Oct12_justgenes.csv", col.names=FALSE, row.names=FALSE)
```

```{r}
clustX <- markerGeneList[grepl('Parenchyma 1',markerGeneList$cluster) | grepl('Parenchyma 2',markerGeneList$cluster),]
#Select just those with at least myAUC of 0.7
clustX <- clustX %>%
  filter(myAUC >= 0.7)

clustX$gene <- gsub('\\-', '_', clustX$gene) #replace dashes in geneid with underscores
table(clustX$gene)
clustX <- unique(clustX$gene)

write.table(x=clustX, file="v10_GO_genelists/Parenchyma-all_Markers_Oct12_justgenes.csv", col.names=FALSE, row.names=FALSE)
```

```{r}
clustX <- markerGeneList[grepl('Protonephridia',markerGeneList$cluster),]
#Select just those with at least myAUC of 0.7
clustX <- clustX %>%
  filter(myAUC >= 0.7)

clustX$gene <- gsub('\\-', '_', clustX$gene) #replace dashes in geneid with underscores
write.table(x=clustX$gene, file="v10_GO_genelists/Protonephridia_Markers_Oct12_justgenes.csv", col.names=FALSE, row.names=FALSE)
```

```{r}
clustX <- markerGeneList[grepl('Stem A',markerGeneList$cluster),]
#Select just those with at least myAUC of 0.7
clustX <- clustX %>%
  filter(myAUC >= 0.7)

clustX$gene <- gsub('\\-', '_', clustX$gene) #replace dashes in geneid with underscores
write.table(x=clustX$gene, file="v10_GO_genelists/Stem-A_Markers_Oct12_justgenes.csv", col.names=FALSE, row.names=FALSE)
```

```{r}
clustX <- markerGeneList[grepl('Stem B',markerGeneList$cluster),]
#Select just those with at least myAUC of 0.7
clustX <- clustX %>%
  filter(myAUC >= 0.7)

clustX$gene <- gsub('\\-', '_', clustX$gene) #replace dashes in geneid with underscores
write.table(x=clustX$gene, file="v10_GO_genelists/Stem-B_Markers_Oct12_justgenes.csv", col.names=FALSE, row.names=FALSE)
```

```{r}
clustX <- markerGeneList[grepl('Stem C',markerGeneList$cluster),]
#Select just those with at least myAUC of 0.7
clustX <- clustX %>%
  filter(myAUC >= 0.7)

clustX$gene <- gsub('\\-', '_', clustX$gene) #replace dashes in geneid with underscores
write.table(x=clustX$gene, file="v10_GO_genelists/Stem-C_Markers_Oct12_justgenes.csv", col.names=FALSE, row.names=FALSE)
```

```{r}
clustX <- markerGeneList[grepl('Stem D',markerGeneList$cluster),]
#Select just those with at least myAUC of 0.7
clustX <- clustX %>%
  filter(myAUC >= 0.7)

clustX$gene <- gsub('\\-', '_', clustX$gene) #replace dashes in geneid with underscores
write.table(x=clustX$gene, file="v10_GO_genelists/Stem-D_Markers_Oct12_justgenes.csv", col.names=FALSE, row.names=FALSE)
```

```{r}
clustX <- markerGeneList[grepl('Stem E',markerGeneList$cluster),]
#Select just those with at least myAUC of 0.7
clustX <- clustX %>%
  filter(myAUC >= 0.7)

clustX$gene <- gsub('\\-', '_', clustX$gene) #replace dashes in geneid with underscores
write.table(x=clustX$gene, file="v10_GO_genelists/Stem-E_Markers_Oct12_justgenes.csv", col.names=FALSE, row.names=FALSE)
```

```{r}
clustX <- markerGeneList[grepl('Stem F',markerGeneList$cluster),]
#Select just those with at least myAUC of 0.7
clustX <- clustX %>%
  filter(myAUC >= 0.7)

clustX$gene <- gsub('\\-', '_', clustX$gene) #replace dashes in geneid with underscores
write.table(x=clustX$gene, file="v10_GO_genelists/Stem-F_Markers_Oct12_justgenes.csv", col.names=FALSE, row.names=FALSE)
```

```{r}
clustX <- markerGeneList[grepl('Stem G',markerGeneList$cluster),]
#Select just those with at least myAUC of 0.7
clustX <- clustX %>%
  filter(myAUC >= 0.7)

clustX$gene <- gsub('\\-', '_', clustX$gene) #replace dashes in geneid with underscores
write.table(x=clustX$gene, file="v10_GO_genelists/Stem-G_Markers_Oct12_justgenes.csv", col.names=FALSE, row.names=FALSE)
```

```{r}
clustX <- markerGeneList[grepl('Stem A',markerGeneList$cluster) | grepl('Stem B',markerGeneList$cluster) | grepl('Stem C',markerGeneList$cluster) | grepl('Stem D',markerGeneList$cluster) | grepl('Stem E',markerGeneList$cluster) | grepl('Stem F',markerGeneList$cluster) | grepl('Stem G',markerGeneList$cluster),]
#Select just those with at least myAUC of 0.7
clustX <- clustX %>%
  filter(myAUC >= 0.7)

clustX$gene <- gsub('\\-', '_', clustX$gene) #replace dashes in geneid with underscores
table(clustX$gene)
clustX <- unique(clustX$gene)

write.table(x=clustX, file="v10_GO_genelists/Stem-all_Markers_Oct12_justgenes.csv", col.names=FALSE, row.names=FALSE)
```

```{r}
clustX <- markerGeneList[grepl('Tegument',markerGeneList$cluster),]
#Select just those with at least myAUC of 0.7
clustX <- clustX %>%
  filter(myAUC >= 0.7)

clustX$gene <- gsub('\\-', '_', clustX$gene) #replace dashes in geneid with underscores
write.table(x=clustX$gene, file="v10_GO_genelists/Tegument_Markers_Oct12_justgenes.csv", col.names=FALSE, row.names=FALSE)
```

Now run these via terminal - takes list of gene IDs and GO type, produces file with significant go terms
```{r}
Rscript TopGO_mira_v10.R Muscle-1_Markers_Oct12_justgenes.csv BP
Rscript TopGO_mira_v10.R Muscle-2_Markers_Oct12_justgenes.csv BP

Rscript TopGO_mira_v10.R Neuron-1_Markers_Oct12_justgenes.csv BP
Rscript TopGO_mira_v10.R Neuron-2_Markers_Oct12_justgenes.csv BP
Rscript TopGO_mira_v10.R Neuron-3_Markers_Oct12_justgenes.csv BP
Rscript TopGO_mira_v10.R Neuron-4_Markers_Oct12_justgenes.csv BP
Rscript TopGO_mira_v10.R Neuron-5_Markers_Oct12_justgenes.csv BP
Rscript TopGO_mira_v10.R Neuron-6_Markers_Oct12_justgenes.csv BP

Rscript TopGO_mira_v10.R Parenchyma-1_Markers_Oct12_justgenes.csv BP
Rscript TopGO_mira_v10.R Parenchyma-2_Markers_Oct12_justgenes.csv BP

Rscript TopGO_mira_v10.R Protonephridia_Markers_Oct12_justgenes.csv BP

Rscript TopGO_mira_v10.R Tegument_Markers_Oct12_justgenes.csv BP

Rscript TopGO_mira_v10.R Stem-A_Markers_Oct12_justgenes.csv BP
Rscript TopGO_mira_v10.R Stem-B_Markers_Oct12_justgenes.csv BP
Rscript TopGO_mira_v10.R Stem-C_Markers_Oct12_justgenes.csv BP
Rscript TopGO_mira_v10.R Stem-D_Markers_Oct12_justgenes.csv BP
Rscript TopGO_mira_v10.R Stem-E_Markers_Oct12_justgenes.csv BP
Rscript TopGO_mira_v10.R Stem-F_Markers_Oct12_justgenes.csv BP
Rscript TopGO_mira_v10.R Stem-G_Markers_Oct12_justgenes.csv BP
```

Now, import the full list of GO results from all the clusters
```{r}
topGO_summary_all <- read.csv("/Users/ta13/R_git/filtered_v10_miracidia/v10_GO_genelists/topGO_summary_miracidia_onv10.csv", stringsAsFactors = FALSE, header = TRUE) #import the marker data from somule papaer
```

```{r}
str(topGO_summary_all)
```
```{r}

new_pal <- c("#9E0059","#007aaa","#ffb703","#c40c18","#fb8500","#7851a9","#00325b","#8ACB88","#107E7D", "#FB6376", "#B3E9C7", "#FFFD82", "#2191FB", "#690500", "#57467B", "#B57F50","#2C514C","#c4b7cb" ,"#69A297" )
```

```{r}
new_pal <- unique(topGO_summary_all$Colour)
table(topGO_summary_all$Colour)
table(topGO_summary_all$Cell.type)

scales::show_col(new_pal)
#fct_reorder(topGO_summary_sporos$Term, topGO_summary_sporos$Cell.type, min)
ggplot(data = topGO_summary_all, aes(x = fct_reorder2(Term, negativelog10FDR, Cell.type), y = negativelog10FDR, fill = Cell.type)) + geom_bar(stat="identity",position = "dodge")+ 
  scale_colour_identity()+
       coord_flip()+theme_bw()+scale_fill_manual(values = new_pal)+ labs(fill = " ", x = " ", y = "-log10FDR")+theme(axis.text.x=element_text(size=15),axis.text.y=element_text(size=12), axis.title.x = element_text(size = 18),legend.key.size = unit(0.8, 'cm'), legend.text = element_text(size=10))
ggsave("v10_GO_genelists/topGO_all_filtv10_plot1_longlist.pdf", width = 20, height = 55, units = c('cm'))
```

```{r}
topGO_summary_sporos_long_2genes <- topGO_summary_all %>%
  filter(str_detect(genes, ","))
```
]
```{r}
ggplot(data = topGO_summary_all, aes(x = fct_reorder2(Term, negativelog10FDR, Cell.type), y = negativelog10FDR, fill = Cell.type)) + geom_bar(stat="identity",position = "dodge")+ 
  scale_colour_identity()+
       coord_flip()+theme_bw()+scale_fill_manual(values = new_pal)+ labs(fill = " ", x = " ", y = "-log10FDR")+theme(axis.text.x=element_text(size=15),axis.text.y=element_text(size=12), axis.title.x = element_text(size = 18),legend.key.size = unit(0.8, 'cm'), legend.text = element_text(size=10))
ggsave("v10_GO_genelists/topGO_all_filtv10_plot1_longlist_twogenes.pdf", width = 20, height = 50, units = c('cm'))
```



