---
title: "import QC sample3 v10"
author: "T Attenborough"
date: "24/11/2022"
output: html_document
---

```{r}
library(Seurat) #Seurat v4.0.2
library(dplyr)
library(patchwork)
library(here)
library(ggplot2)
library(clustree)
library(ggrepel)
library(tidyseurat)
library(RColorBrewer)
library(SingleCellExperiment)
library(scater)
library(DoubletFinder)
```

First I am going to look at sample 3 from MIRACIDIA run 1

```{r}
run1.v10.sample3.unsorted.filt <- readRDS(file = "/Users/ta13/R_tutorials/neat_miracidia/run1.v10.sample3.unsorted.filt.rds")

```


Import all run1.v10 sample3 (unsorted)
```{r}
run1.v10.sample3.mira.data <- Read10X(here(c('/Users/ta13/Miracidia/v10_filtered/Sample3/filtered_feature_bc_matrix/')))
```
Initially there are 11,611 cells.

Import into a Seurat object, removing any genes which don't appear in at least 3 cells, and any cells which express less than 200 genes.
```{r}
run1.v10.sample3.unsorted <- CreateSeuratObject(counts = run1.v10.sample3.mira.data, project = "run1.v10.sample3.unsorted", min.cells = 3, min.features = 200)
```
Now 11,611 cells and 8,869 genes.

Once you have created the Seurat object, the count matrices and individual count matrices and objects are not needed anymore. It is a good idea to remove them and run garbage collect to free up some memory.
```{r}
# remove all objects that will not be used.
rm(run1.v10.sample3.mira.data)

# run garbage collect to free up memory
gc()
```


Add metadata to the Seurat object
```{r}
#add metadata
run1.v10.sample3.unsorted@meta.data$plex =  "sample3"

table(run1.v10.sample3.unsorted$plex)

#add metadata
run1.v10.sample3.unsorted@meta.data$type =  "unsorted"

table(run1.v10.sample3.unsorted$type)

#add metadata
run1.v10.sample3.unsorted@meta.data$stage =  "miracidia"

table(run1.v10.sample3.unsorted$stage)
```

Plot raw QC
```{r}
run1.v10.sample3.unsorted[["percent.mt"]] <- PercentageFeatureSet(run1.v10.sample3.unsorted, pattern = "Smp-9")
VlnPlot(run1.v10.sample3.unsorted, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), ncol = 3)
```

Look at how number or UMIs and number of genes intersect, also with mitochondrial percentage. Also calculate the log10 genes per UMI, and make a metadata object.
```{r}
FeatureScatter(object = run1.v10.sample3.unsorted, feature1 = "nCount_RNA", feature2 = "nFeature_RNA")+
  	ggtitle("Genes and UMIs in each cell")

run1.v10.sample3.unsorted$log10GenesPerUMI <- log10(run1.v10.sample3.unsorted$nFeature_RNA) / log10(run1.v10.sample3.unsorted$nCount_RNA)
run1.v10.sample3.unsorted_metadata <- run1.v10.sample3.unsorted@meta.data
run1.v10.sample3.unsorted_metadata$cells <- rownames(run1.v10.sample3.unsorted_metadata)
run1.v10.sample3.unsorted@meta.data <- run1.v10.sample3.unsorted_metadata

FeatureScatter(run1.v10.sample3.unsorted, "nCount_RNA", "percent.mt", group.by = "orig.ident", pt.size = 0.5)

FeatureScatter(run1.v10.sample3.unsorted, "nFeature_RNA", "percent.mt", group.by = "orig.ident", pt.size = 0.5)

```

For high quality data, the proportional histogram should contain a single large peak that represents cells that were encapsulated. If we see a small shoulder to the right of the major peak (not present in our data), or a bimodal distribution of the cells, that can indicate a couple of things. It might be that there are a set of cells that failed for some reason. It could also be that there are biologically different types of cells (i.e. quiescent cell populations, less complex cells of interest), and/or one type is much smaller than the other (i.e. cells with high counts may be cells that are larger in size). Therefore, this threshold should be assessed with other metrics. (From HBCTraining page)

```{r}
# Visualize the number of cell counts per sample
run1.v10.sample3.unsorted_metadata %>% 
  	ggplot(aes(x=plex, fill=plex)) + 
  	geom_bar() +
  	theme_classic() +
  	theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
  	theme(plot.title = element_text(hjust=0.5, face="bold")) +
  	ggtitle("Number of Cells")

# Visualize the number UMIs/transcripts per cell. We want to have at least 500 UMIs/cell if possible. Black lines at 500 and 100 UMIs
run1.v10.sample3.unsorted_metadata %>% 
  	ggplot(aes(color=plex, x=nCount_RNA, fill= plex)) + 
  	geom_density(alpha = 0.2) + 
  	scale_x_log10() + 
  	theme_classic() +
  	ylab("Cell density") +
    geom_vline(xintercept = 100) +
  	geom_vline(xintercept = 500) +
  	geom_vline(xintercept = 1000)+
  	ggtitle("UMIs per cell")
```

```{r}
# Visualize the distribution of genes detected per cell via histogram
run1.v10.sample3.unsorted_metadata %>% 
  	ggplot(aes(color=plex, x=nFeature_RNA, fill= plex)) + 
  	geom_density(alpha = 0.2) + 
  	theme_classic() +
  	scale_x_log10() + 
  	geom_vline(xintercept = 300)+
  	ggtitle("Genes per cell")


# Visualize the distribution of genes detected per cell via boxplot
run1.v10.sample3.unsorted_metadata %>% 
  	ggplot(aes(x=plex, y=log10(nFeature_RNA), fill=plex)) + 
  	geom_boxplot() + 
  	theme_classic() +
  	theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
  	theme(plot.title = element_text(hjust=0.5, face="bold")) +
  	ggtitle("Log10 of gene count per cell")

```
```{r}
# Visualize the correlation between genes detected and number of UMIs and determine whether strong presence of cells with low numbers of genes/UMIs
run1.v10.sample3.unsorted_metadata %>% 
  	ggplot(aes(x=nCount_RNA, y=nFeature_RNA, color=percent.mt)) + 
  	geom_point() + 
	scale_colour_gradient(low = "gray90", high = "black") +
  	stat_smooth(method=lm) +
  	scale_x_log10() + 
  	scale_y_log10() + 
  	theme_classic() +
  	geom_vline(xintercept = 1000) +
  	geom_hline(yintercept = 500) +
  	ggtitle("UMI v gene count per cell, coloured by mito%")

run1.v10.sample3.unsorted_metadata %>% 
  	ggplot(aes(x=nCount_RNA, y=nFeature_RNA, color=percent.mt)) + 
  	geom_point() + 
	scale_colour_gradient(low = "gray90", high = "black") +
  	stat_smooth(method=lm) +
  	scale_x_log10() + 
  	scale_y_log10() + 
  	theme_classic() +
  	geom_vline(xintercept = 1000) +
  	geom_hline(yintercept = 500) +
  	facet_wrap(~plex)

run1.v10.sample3.unsorted_metadata %>% 
  	ggplot(aes(x=percent.mt, y=nFeature_RNA, color=nCount_RNA)) + 
  	geom_point() + 
	scale_colour_gradient(low = "gray90", high = "black") +
  	stat_smooth(method=lm) +
  	scale_x_log10() + 
  	scale_y_log10() + 
  	theme_classic() +
  	geom_vline(xintercept = 1000) +
  	geom_hline(yintercept = 500) +
  	ggtitle("Mito v gene count per cell, coloured by readcount")
```

```{r}
# Visualize the distribution of mitochondrial gene expression detected per cell
run1.v10.sample3.unsorted_metadata %>% 
  	ggplot(aes(color=plex, x=percent.mt, fill=plex)) + 
  	geom_density(alpha = 0.2) + 
  	scale_x_log10() + 
  	theme_classic() +
  	geom_vline(xintercept = 5)+
  	ggtitle("Cell density by mito%")

```

Look at cell complexity: in samples where each cell is sequenced less, it will have a higher complexity as the sequencing has not started to become saturated. For cells with complexity, this may be enough to approach saturation. Therefore these cells may be detected through low novelty scores. In an example, most cells had a novelty score above 0.8. From HBCTraining.
```{r}
# Visualize the overall complexity of the gene expression by visualizing the genes detected per UMI
run1.v10.sample3.unsorted_metadata %>%
  	ggplot(aes(x=log10GenesPerUMI, color = plex, fill=plex)) +
  	geom_density(alpha = 0.2) +
  	theme_classic() +
  	geom_vline(xintercept = 0.8)
```

Filter out cells with more than 5% mitochondrial gene expression and less than 500 UMIs, 

Should I also consider:
Lowering/changing the mito %? 
putting a ceiling on number of genes/UMIs?
and complexity less than 0.8?

Min features is 300, set earlier when importing the seurat object
```{r}
run1.v10.sample3.unsorted <- subset(run1.v10.sample3.unsorted, subset = percent.mt < 5)

dim(run1.v10.sample3.unsorted) #shows number of genes and number of cells

run1.v10.sample3.unsorted <- subset(run1.v10.sample3.unsorted, subset = nCount_RNA > 500)

dim(run1.v10.sample3.unsorted) #shows number of genes and number of cells

#run1.v10.sample3.unsorted <- subset(run1.v10.sample3.unsorted, subset = log10GenesPerUMI > 0.80)
#dim(run1.v10.sample3.unsorted) #shows number of genes and number of cells

```
Now there are 8869 genes and 11,461 cells


Plot filtered QC
Lets plot the same QC-stats another time. Actually, let's re-plot some more of them too!!
```{r}
feats <- c("nFeature_RNA", "nCount_RNA", "percent.mt")
run1.v10.sample3.unsorted$log10GenesPerUMI <- log10(run1.v10.sample3.unsorted$nFeature_RNA) / log10(run1.v10.sample3.unsorted$nCount_RNA)
run1.v10.sample3.unsorted_metadata <- run1.v10.sample3.unsorted@meta.data
run1.v10.sample3.unsorted_metadata$cells <- rownames(run1.v10.sample3.unsorted_metadata)
run1.v10.sample3.unsorted@meta.data <- run1.v10.sample3.unsorted_metadata

VlnPlot(run1.v10.sample3.unsorted, group.by = "orig.ident", features = feats, pt.size = 0.1, ncol = 3) + 
    NoLegend()

FeatureScatter(object = run1.v10.sample3.unsorted, feature1 = "nCount_RNA", feature2 = "nFeature_RNA")+
  	ggtitle("Genes and UMIs in each cell")

FeatureScatter(run1.v10.sample3.unsorted, "nCount_RNA", "percent.mt", group.by = "orig.ident", pt.size = 0.5)

FeatureScatter(run1.v10.sample3.unsorted, "nFeature_RNA", "percent.mt", group.by = "orig.ident", pt.size = 0.5)

# Visualize the number of cell counts per sample
run1.v10.sample3.unsorted_metadata %>% 
  	ggplot(aes(x=plex, fill=plex)) + 
  	geom_bar() +
  	theme_classic() +
  	theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
  	theme(plot.title = element_text(hjust=0.5, face="bold")) +
  	ggtitle("Number of Cells")

# Visualize the number UMIs/transcripts per cell. We want to have at least 500 UMIs/cell if possible. Black lines at 500 and 100 UMIs
run1.v10.sample3.unsorted_metadata %>% 
  	ggplot(aes(color=plex, x=nCount_RNA, fill= plex)) + 
  	geom_density(alpha = 0.2) + 
  	scale_x_log10() + 
  	theme_classic() +
  	ylab("Cell density") +
  	geom_vline(xintercept = 500) +
  	geom_vline(xintercept = 1000)+
  	ggtitle("UMIs per cell")

# Visualize the distribution of genes detected per cell via histogram
run1.v10.sample3.unsorted_metadata %>% 
  	ggplot(aes(color=plex, x=nFeature_RNA, fill= plex)) + 
  	geom_density(alpha = 0.2) + 
  	theme_classic() +
  	scale_x_log10() + 
  	geom_vline(xintercept = 300)+
  	ggtitle("Genes per cell")

# Visualize the distribution of genes detected per cell via boxplot
run1.v10.sample3.unsorted_metadata %>% 
  	ggplot(aes(x=plex, y=log10(nFeature_RNA), fill=plex)) + 
  	geom_boxplot() + 
  	theme_classic() +
  	theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
  	theme(plot.title = element_text(hjust=0.5, face="bold")) +
  	ggtitle("Log10 of gene count per cell")

# Visualize the correlation between genes detected and number of UMIs and determine whether strong presence of cells with low numbers of genes/UMIs
run1.v10.sample3.unsorted_metadata %>% 
  	ggplot(aes(x=nCount_RNA, y=nFeature_RNA, color=percent.mt)) + 
  	geom_point() + 
	scale_colour_gradient(low = "gray90", high = "black") +
  	stat_smooth(method=lm) +
  	scale_x_log10() + 
  	scale_y_log10() + 
  	theme_classic() +
  	geom_vline(xintercept = 1000) +
  	geom_hline(yintercept = 500) +
  	ggtitle("UMI v gene count per cell, coloured by mito%")

run1.v10.sample3.unsorted_metadata %>% 
  	ggplot(aes(x=nCount_RNA, y=nFeature_RNA, color=percent.mt)) + 
  	geom_point() + 
	scale_colour_gradient(low = "gray90", high = "black") +
  	stat_smooth(method=lm) +
  	scale_x_log10() + 
  	scale_y_log10() + 
  	theme_classic() +
  	geom_vline(xintercept = 1000) +
  	geom_hline(yintercept = 500) +
  	facet_wrap(~plex)

run1.v10.sample3.unsorted_metadata %>% 
  	ggplot(aes(x=percent.mt, y=nFeature_RNA, color=nCount_RNA)) + 
  	geom_point() + 
	scale_colour_gradient(low = "gray90", high = "black") +
  	stat_smooth(method=lm) +
  	scale_x_log10() + 
  	scale_y_log10() + 
  	theme_classic() +
  	geom_vline(xintercept = 1000) +
  	geom_hline(yintercept = 500) +
  	ggtitle("UMI v gene count per cell, coloured by readcount")

# Visualize the distribution of mitochondrial gene expression detected per cell
run1.v10.sample3.unsorted_metadata %>% 
  	ggplot(aes(color=plex, x=percent.mt, fill=plex)) + 
  	geom_density(alpha = 0.2) + 
  	scale_x_log10() + 
  	theme_classic() +
  	geom_vline(xintercept = 5)+
  	ggtitle("Cell density by mito%")

# Visualize the overall complexity of the gene expression by visualizing the genes detected per UMI
run1.v10.sample3.unsorted_metadata %>%
  	ggplot(aes(x=log10GenesPerUMI, color = plex, fill=plex)) +
  	geom_density(alpha = 0.2) +
  	theme_classic() +
  	geom_vline(xintercept = 0.8)
```


Then, let's save the new metadata file
```{r}
 # Save filtered subset to new metadata
run1.v10.sample3.unsorted.metadata_initialFilt <- run1.v10.sample3.unsorted@meta.data
```

Predict doublets
Have to do initial normalisation and clustering before doublets can be addressed
```{r}
run1.v10.sample3.unsorted <- NormalizeData(run1.v10.sample3.unsorted)
run1.v10.sample3.unsorted <- FindVariableFeatures(run1.v10.sample3.unsorted, selection.method = "vst", nfeatures = 2000)
# Identify the 10 most highly variable genes
top10 <- head(VariableFeatures(run1.v10.sample3.unsorted), 10)
top10

all.genes <- rownames(run1.v10.sample3.unsorted)
run1.v10.sample3.unsorted <- ScaleData(run1.v10.sample3.unsorted, features = all.genes, vars.to.regress = c("percent.mt"))
```

```{r}
#Check how many PCs to use for the data using Mathews Molecular cross validation
source("/Users/ta13/R_tutorials/sporocysts/code.R")
mcv = molecularCrossValidation(run1.v10.sample3.unsorted@assays$RNA@counts, varGenes = VariableFeatures(run1.v10.sample3.unsorted),normalisation = minimalSeuratV3)

plotMCV(mcv)
```
Indicates 23 PCs min

Now, perform dimensionality reduction by PCA and UMAP embedding

Here, we perform PCA on the scaled data. The most variable features selected earlier are used.
```{r}
run1.v10.sample3.unsorted <- RunPCA(run1.v10.sample3.unsorted, features = VariableFeatures(object = run1.v10.sample3.unsorted)) #shows top contributing features for the PCs
VizDimLoadings(run1.v10.sample3.unsorted, dims = 1:2, reduction = "pca") #shows the weightings of top contributing features to pcs 1 and 2
DimHeatmap(run1.v10.sample3.unsorted, dims = 1, cells = 500, balanced = TRUE) #plots heatmap of top 500 mist variable cells for PC1, with relative gene expression
#DimHeatmap(run1.v10.sample3.unsorted, dims = 1:15, cells = 500, balanced = TRUE) #this gives the heatmaps for PCs 1-15, so you can visually inspect the genes/PCs

```

Use JackStraw to randomly permute data in 1% chunks. Here with 100 replicates and for 50 PCs
```{r}
run1.v10.sample3.unsorted <- JackStraw(run1.v10.sample3.unsorted, num.replicate = 100, dims =50) #do the permutation
run1.v10.sample3.unsorted <- ScoreJackStraw(run1.v10.sample3.unsorted, dims = 1:50) #extract the scores
JackStrawPlot(run1.v10.sample3.unsorted, dims = 1:50) #plot the p-vals for PCs. Dashed line giives null distribution
ggsave("run1.v10.sample3_jackstrawplot.pdf", width = 30, height = 15, units = c('cm'))

ElbowPlot(run1.v10.sample3.unsorted, ndims = 50)  #ranks PCs by percentage of variation. A clear dropoff is sometimes seen, though not really here.
ggsave("run1.v10.sample3_elbowplot.pdf")

```

Next comes clustering and plotting of clusters.
```{r}
run1.v10.sample3.unsorted <- FindNeighbors(run1.v10.sample3.unsorted, dims = 1:33) #here construct k-nearst neighbours graoh based on euclidean distance in PCA space, then refine edge weights based on Jaccard similarity. this takes the number of PCs previously determined as importan (here 15 PCs_)
run1.v10.sample3.unsorted <- FindClusters(run1.v10.sample3.unsorted, resolution = 0.5) #this iteratively groups cells using Louvain algorithm (default). Resolution sets the granularity. 0.4-1.2 gives good results for ~3K cells, with larger number suiting larger datasets.

# Select a range of resolutions
resolution.range <- seq(from = 0, to = 2, by = 0.1)

# Find clusters using a range of resolutions
run1.v10.sample3.unsorted <- Seurat::FindClusters(object = run1.v10.sample3.unsorted, resolution = resolution.range)

clustree(run1.v10.sample3.unsorted)
ggsave("run1.v10.sample3.unsortedclust_33PC_0_to_2_tree_RNA.pdf", width = 20, height = 30, units = c('cm'))
```

Based on the clustree results, I am going to choose an initial res of 0.7 with 40PCs

```{r}
run1.v10.sample3.unsorted <- FindClusters(run1.v10.sample3.unsorted, resolution = 0.7) #this iteratively groups cells using Louvain algorithm (default). Resolution sets the granularity. 0.4-1.2 gives good results for ~3K cells, with larger number suiting larger datasets.
run1.v10.sample3.unsorted <- RunUMAP(run1.v10.sample3.unsorted, dims = 1:33) #runs umap to visualise the clusters. Need to set the number of PCs
DimPlot(run1.v10.sample3.unsorted, reduction = "umap", label=T) #visulaises the UMAP
ggsave("run1.v10.sample3.unsortedclust_33PC_0.7res_batchRegressed_after1filt.pdf")

FeaturePlot(run1.v10.sample3.unsorted, features="nCount_RNA", label=TRUE)
ggsave("run1.v10.sample3.unsortedclust_33PC_0.7res_UMIs.pdf")

```


Now, use DoubletFinder to find and remove doublets.

PK identification: find the optimum neighbourhood size to calculate pANN
```{r}
sweep.res.list_run1.v10.sample3.unsorted <- paramSweep_v3(run1.v10.sample3.unsorted, PCs = 1:33, sct = FALSE)

sweep.stats_run1.v10.sample3.unsorted <- summarizeSweep(sweep.res.list_run1.v10.sample3.unsorted, GT = FALSE)
bcmvn_run1.v10.sample3.unsorted <- find.pK(sweep.stats_run1.v10.sample3.unsorted)

#stats sweeps currently estimates that the optimum pK for these data is... 0.02 and pN = 0.05

annotations <- run1.v10.sample3.unsorted@meta.data$RNA_snn_res.0.7
nExp_poi <- round(0.528*nrow(run1.v10.sample3.unsorted@meta.data)) # assuming 10X loading to recover 10,000 cells
homotypic.prop <- modelHomotypic(annotations)
nExp_poi.adj <- round(nExp_poi*(1-homotypic.prop))

pK=as.numeric(as.character(bcmvn_run1.v10.sample3.unsorted$pK))
BCmetric=bcmvn_run1.v10.sample3.unsorted$BCmetric
pK_choose = pK[which(BCmetric %in% max(BCmetric))]

par(mar=c(5,4,4,8)+1,cex.main=1.2,font.main=2)
plot(x = pK, y = BCmetric, pch = 16,type="b",
col = "blue",lty=1)
abline(v=pK_choose,lwd=2,col='red',lty=2)
title("The BCmvn distributions")
text(pK_choose,max(BCmetric),as.character(pK_choose),pos = 4,col = "red")

## Run DoubletFinder  ----------------------------------------------------------------
run1.v10.sample3.unsorted <- doubletFinder_v3(run1.v10.sample3.unsorted, PCs = 1:33, pN = 0.25, pK = 	0.27, nExp = nExp_poi.adj, reuse.pANN = FALSE, sct = FALSE)

table(run1.v10.sample3.unsorted$DF.classifications_0.25_0.27_5496) #shows number of genes and number of cells


DimPlot(run1.v10.sample3.unsorted, reduction = "umap", group.by = "DF.classifications_0.25_0.27_5496") #visulaises the UMAP
ggsave("run1.v10.sample3.unsorted_doublets_52.pdf")



```

We should expect that two cells have more detected genes than a single cell, lets check if our predicted doublets also have more detected genes in general.
```{r}
VlnPlot(run1.v10.sample3.unsorted, features = "nFeature_RNA", group.by = 'DF.classifications_0.25_0.27_5496', pt.size = 0.1)

FeatureScatter(run1.v10.sample3.unsorted, "nFeature_RNA", "nCount_RNA", group.by = "DF.classifications_0.25_0.27_5496", pt.size = 0.5)

```

```{r}

run1.v10.sample3.unsorted.metadata <- run1.v10.sample3.unsorted@meta.data

ggplot(run1.v10.sample3.unsorted.metadata, aes(nFeature_RNA, pANN_0.25_0.27_5496, color=DF.classifications_0.25_0.27_5496)) + geom_point()
ggsave("run1.v10.sample3.unsorted.df_scores_0.528.pdf")
```


Now, lets remove all predicted doublets from our data. I also so want to save the doublets, to see what's in them later, just in case.
```{r}
run1.v10.sample3.unsorted.filt = run1.v10.sample3.unsorted[, run1.v10.sample3.unsorted@meta.data[, 'DF.classifications_0.25_0.27_5496'] == "Singlet"]
run1.v10.sample3.unsorted.doublets = run1.v10.sample3.unsorted[, run1.v10.sample3.unsorted@meta.data[, 'DF.classifications_0.25_0.27_5496'] == "Doublet"]

dim(run1.v10.sample3.unsorted.filt)

```

Leaves 5965 cells and 8869 genes

 Save the doublet-free data, and the doublets
```{r}
#saveRDS(run1.v10.sample3.unsorted.filt, file = "run1.v10.sample3.unsorted_afterDF.rds") #saves this version of the dataset
saveRDS(run1.v10.sample3.unsorted.doublets, file = "run1.v10.sample3.unsorted_doublets_52.rds") #saves this version of the dataset

```

Now, rerun the visual QC.
```{r}
feats <- c("nFeature_RNA", "nCount_RNA", "percent.mt")
run1.v10.sample3.unsorted.filt$log10GenesPerUMI <- log10(run1.v10.sample3.unsorted.filt$nFeature_RNA) / log10(run1.v10.sample3.unsorted.filt$nCount_RNA)
run1.v10.sample3.unsorted.filt_metadata <- run1.v10.sample3.unsorted.filt@meta.data
run1.v10.sample3.unsorted.filt_metadata$cells <- rownames(run1.v10.sample3.unsorted.filt_metadata)
run1.v10.sample3.unsorted.filt@meta.data <- run1.v10.sample3.unsorted.filt_metadata

VlnPlot(run1.v10.sample3.unsorted.filt, group.by = "orig.ident", features = feats, pt.size = 0.1, ncol = 3) + 
  NoLegend()

FeatureScatter(object = run1.v10.sample3.unsorted.filt, feature1 = "nCount_RNA", feature2 = "nFeature_RNA")+
  ggtitle("Genes and UMIs in each cell")

FeatureScatter(run1.v10.sample3.unsorted.filt, "nCount_RNA", "percent.mt", group.by = "orig.ident", pt.size = 0.5)

FeatureScatter(run1.v10.sample3.unsorted.filt, "nFeature_RNA", "percent.mt", group.by = "orig.ident", pt.size = 0.5)

# Visualize the number of cell counts per sample
run1.v10.sample3.unsorted.filt_metadata %>% 
  ggplot(aes(x=plex, fill=plex)) + 
  geom_bar() +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
  theme(plot.title = element_text(hjust=0.5, face="bold")) +
  ggtitle("Number of Cells")

# Visualize the number UMIs/transcripts per cell. We want to have at least 500 UMIs/cell if possible. Black lines at 500 and 100 UMIs
run1.v10.sample3.unsorted.filt_metadata %>% 
  ggplot(aes(color=plex, x=nCount_RNA, fill= plex)) + 
  geom_density(alpha = 0.2) + 
  scale_x_log10() + 
  theme_classic() +
  ylab("Cell density") +
  geom_vline(xintercept = 500) +
  geom_vline(xintercept = 1000)+
  ggtitle("UMIs per cell")

# Visualize the distribution of genes detected per cell via histogram
run1.v10.sample3.unsorted.filt_metadata %>% 
  ggplot(aes(color=plex, x=nFeature_RNA, fill= plex)) + 
  geom_density(alpha = 0.2) + 
  theme_classic() +
  scale_x_log10() + 
  geom_vline(xintercept = 300)+
  ggtitle("Genes per cell")


# Visualize the distribution of genes detected per cell via boxplot
run1.v10.sample3.unsorted.filt_metadata %>% 
  ggplot(aes(x=plex, y=log10(nFeature_RNA), fill=plex)) + 
  geom_boxplot() + 
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
  theme(plot.title = element_text(hjust=0.5, face="bold")) +
  ggtitle("Log10 of gene count per cell")

# Visualize the correlation between genes detected and number of UMIs and determine whether strong presence of cells with low numbers of genes/UMIs
run1.v10.sample3.unsorted.filt_metadata %>% 
  ggplot(aes(x=nCount_RNA, y=nFeature_RNA, color=percent.mt)) + 
  geom_point() + 
  scale_colour_gradient(low = "gray90", high = "black") +
  stat_smooth(method=lm) +
  scale_x_log10() + 
  scale_y_log10() + 
  theme_classic() +
  geom_vline(xintercept = 1000) +
  geom_hline(yintercept = 500) +
  ggtitle("UMI v gene count per cell, coloured by mito%")


run1.v10.sample3.unsorted.filt_metadata %>% 
  ggplot(aes(x=nCount_RNA, y=nFeature_RNA, color=percent.mt)) + 
  geom_point() + 
  scale_colour_gradient(low = "gray90", high = "black") +
  stat_smooth(method=lm) +
  scale_x_log10() + 
  scale_y_log10() + 
  theme_classic() +
  geom_vline(xintercept = 1000) +
  geom_hline(yintercept = 500) +
  facet_wrap(~plex)


run1.v10.sample3.unsorted.filt_metadata %>% 
  ggplot(aes(x=percent.mt, y=nFeature_RNA, color=nCount_RNA)) + 
  geom_point() + 
  scale_colour_gradient(low = "gray90", high = "black") +
  stat_smooth(method=lm) +
  scale_x_log10() + 
  scale_y_log10() + 
  theme_classic() +
  geom_vline(xintercept = 1000) +
  geom_hline(yintercept = 500) +
  ggtitle("UMI v gene count per cell, coloured by readcount")

# Visualize the distribution of mitochondrial gene expression detected per cell
run1.v10.sample3.unsorted.filt_metadata %>% 
  ggplot(aes(color=plex, x=percent.mt, fill=plex)) + 
  geom_density(alpha = 0.2) + 
  scale_x_log10() + 
  theme_classic() +
  geom_vline(xintercept = 5)+
  ggtitle("Cell density by mito%")

# Visualize the overall complexity of the gene expression by visualizing the genes detected per UMI
run1.v10.sample3.unsorted.filt_metadata %>%
  ggplot(aes(x=log10GenesPerUMI, color = plex, fill=plex)) +
  geom_density(alpha = 0.2) +
  theme_classic() +
  geom_vline(xintercept = 0.8)

```

Use SingleCellExperiment to look at the top genes, if that will now work.
```{r}
mito_genes <- rownames(run1.v10.sample3.unsorted.filt)[grep("^Smp-9", rownames(run1.v10.sample3.unsorted.filt))]

run1.v10.sample3.unsorted.sce <- as.SingleCellExperiment(run1.v10.sample3.unsorted.filt)
run1.v10.sample3.unsorted.sce <- perCellQCMetrics(run1.v10.sample3.unsorted.sce)

plotHighestExprs(run1.v10.sample3.unsorted.sce, exprs_values = "counts")
ggsave("top50_mostExpressedGenes_run1.v10.sample3.unsorted.pdf", width = 20, height = 15, units = c('cm'))
```

Now, will will perfrom SCTransfrom on the data, and cluster again.
I am going to use sctransform, which takes the place of NormalizeData, FindVariableFeatures, and ScaleData, takes into account variablitity in sequencing depth, and allows to regress out percent.mt.
```{r}
# run sctransform
run1.v10.sample3.unsorted.filt <- SCTransform(run1.v10.sample3.unsorted.filt, vars.to.regress = c("percent.mt"), verbose = FALSE, return.only.var.genes = FALSE)
```

```{r}
run1.v10.sample3.unsorted <- run1.v10.sample3.unsorted %>% 
    SCTransform(vars.to.regress = "percent.mt") %>% RunPCA() %>% FindNeighbors(dims = 1:30) %>% 
    RunUMAP(dims = 1:30) %>% FindClusters()
```

Here, we perform PCA on the scaled data. The most variable features selected earlier are used.
```{r}
#DefaultAssay(run1.v10.sample3.unsorted) <- "SCT"


run1.v10.sample3.unsorted.filt <- RunPCA(run1.v10.sample3.unsorted.filt, features = VariableFeatures(object = run1.v10.sample3.unsorted.filt)) #shows top contributing features for the PCs
VizDimLoadings(run1.v10.sample3.unsorted.filt, dims = 1:2, reduction = "pca") #shows the weightings of top contributing features to pcs 1 and 2
DimHeatmap(run1.v10.sample3.unsorted.filt, dims = 1, cells = 500, balanced = TRUE) #plots heatmap of top 500 mist variable cells for PC1, with relative gene expression

ElbowPlot(run1.v10.sample3.unsorted.filt, ndims = 50)  #ranks PCs by percentage of variation. A clear dropoff is sometimes seen, though not really here.

```

```{r}
#Check how many PCs to use for the data using Mathews Molecular cross validation
source("/Users/ta13/R_tutorials/sporocysts/code.R")
mcv = molecularCrossValidation(run1.v10.sample3.unsorted.filt@assays$RNA@counts, varGenes = VariableFeatures(run1.v10.sample3.unsorted.filt),normalisation = minimalSeuratV3)

plotMCV(mcv)
```
Indicates 16 PCs min (one less than v9)

Next comes clustering and plotting of clusters.
```{r}
run1.v10.sample3.unsorted.filt <- FindNeighbors(run1.v10.sample3.unsorted.filt, dims = 1:40) #here construct k-nearst neighbours graoh based on euclidean distance in PCA space, then refine edge weights based on Jaccard similarity. this takes the number of PCs previously determined as importan (here 15 PCs_)
run1.v10.sample3.unsorted.filt <- FindClusters(run1.v10.sample3.unsorted.filt, resolution = 0.5) #this iteratively groups cells using Louvain algorithm (default). Resolution sets the granularity. 0.4-1.2 gives good results for ~3K cells, with larger number suiting larger datasets.



# Select a range of resolutions
resolution.range <- seq(from = 0, to = 2, by = 0.2)

# Find clusters using a range of resolutions
run1.v10.sample3.unsorted.filt <- Seurat::FindClusters(object = run1.v10.sample3.unsorted.filt, resolution = resolution.range)

clustree(run1.v10.sample3.unsorted.filt)
ggsave("run1.v10.sample3.unsorted.filt.clust_40PC_0_to_2_tree_SCT_52.pdf", width = 20, height = 30, units = c('cm'))
```


Based on the clustree results, I am going to choose an res of 0.8 with 40PCs

```{r}
run1.v10.sample3.unsorted.filt <- FindClusters(run1.v10.sample3.unsorted.filt, resolution = 1.2) #this iteratively groups cells using Louvain algorithm (default). Resolution sets the granularity. 0.4-1.2 gives good results for ~3K cells, with larger number suiting larger datasets.
run1.v10.sample3.unsorted.filt <- RunUMAP(run1.v10.sample3.unsorted.filt, dims = 1:40) #runs umap to visualise the clusters. Need to set the number of PCs
DimPlot(run1.v10.sample3.unsorted.filt, reduction = "umap", label=T) #visulaises the UMAP
ggsave("run1.v10.sample3.unsorted.filtclust_40PC_1.2res_mtRegressed__after2filt_SCT_52.pdf")

FeaturePlot(run1.v10.sample3.unsorted.filt, features="percent.mt", label=TRUE)
ggsave("run1.v10.sample3.unsorted.filt_40PC_1.2res_mt_SCT_52.pdf")

FeaturePlot(run1.v10.sample3.unsorted.filt, features="nCount_RNA", label=TRUE)
ggsave("run1.v10.sample3.unsorted.filt_40PC_1.2res_UMIs_SCT_52.pdf")

FeaturePlot(run1.v10.sample3.unsorted.filt, features="nFeature_RNA", label=TRUE)
ggsave("run1.v10.sample3.unsorted.filt_40PC_1.2res_genes_SCT_52.pdf")
```

Now, import the final somule data object from Carmen
```{r}
somules <- readRDS(file = "/Users/ta13/R_tutorials/sporocysts/V9_no_CDSUTR_Tess_Carmen 2/data/Seurat_Object/Final_objects/somules.RDS")
```

Use somule data to initially project annotations onto miracidia run1.v10 unsorted data
```{r}
DefaultAssay(run1.v10.sample3.unsorted.filt) <- "RNA"

#This is for label transfer
pair.anchors <- FindTransferAnchors(reference = somules, query = run1.v10.sample3.unsorted.filt, dims = 1:40, features = intersect(VariableFeatures(somules), VariableFeatures(run1.v10.sample3.unsorted.filt)))

predictions <- TransferData(anchorset = pair.anchors, refdata = Idents(somules), dims = 1:40)

run1.v10.sample3.unsorted.filt <- AddMetaData(run1.v10.sample3.unsorted.filt, metadata = predictions)
DimPlot(run1.v10.sample3.unsorted.filt, group.by = 'predicted.id', label = T, label.size = 2)
ggsave("run1.v10.sample3.unsorted.filt_labels_from_somules_SCT_mtRegressed52.pdf")

DimPlot(run1.v10.sample3.unsorted.filt, reduction = "umap", group.by = "plex") #visulaises the UMAP
ggsave("run1.v10.sample3.unsorted.filt_PC38_res0.8_batchRegressed_SCT.pdf")
```

Extract top marker from the object
```{r}
DefaultAssay(run1.v10.sample3.unsorted.filt) <- "RNA"

#Find markers roc
run1.v10.sample3.unsorted.filt.markers_roc_RNA <- FindAllMarkers(run1.v10.sample3.unsorted.filt, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25, test.use = "roc")

run1.v10.sample3.unsorted.filt.top5_roc_RNA=run1.v10.sample3.unsorted.filt.markers_roc_RNA %>% group_by(cluster) %>% top_n(n = 5, wt = myAUC)# groups the markers by cluster, then picks the top 5 most differentiually expressed markers
write.csv(x=run1.v10.sample3.unsorted.filt.top5_roc_RNA, file="top5_markerz_roc_run1.v10.sample3.unsorted.filt_SCT.csv")
```

Clust 16 is the most MT-y

Then, let's save the new metadata file
```{r}
 # Save filtered subset to new metadata
run1.v10.sample3.unsorted.filt.metadata <- run1.v10.sample3.unsorted.filt@meta.data

run1.v10.sample3.unsorted.filt@misc$allmarkersSCT <- run1.v10.sample3.unsorted.filt.markers_roc_RNA

```

Here's lets save the filtered object for future use
```{r}
saveRDS(run1.v10.sample3.unsorted.filt, file = "run1.v10.sample3.unsorted.filt_52.rds") #saves this version of the dataset

```

This object should now be ready to integrate with the other samples.