---
title: "prep_all_sporo_for_scvelo"
author: "T Attenborough"
date: "16/01/2023"
output: html_document
---

```{r, message=FALSE}
library(remotes)
library(Seurat)
library(zeallot) # For %<-% that unpacks lists in the Python manner
library(DropletUtils)
library(tidyverse)
library(GGally) # For ggpairs
library(scales)
library(plotly)
library(BUSpaRse)
library(SeuratWrappers)
library(SeuratData)
library(SeuratDisk)
theme_set(theme_bw())
```

```{r}
sporo.big.forvelo <- merge(commCells_sample1, y = c(commCells_sample2, commCells_sample4, commCells_sample3), add.cell.ids = c("FUGI_R_D7465034", "FUGI_R_D7465035", "FUGI_R_D7465036", "FUGI_R_D7465037"), project = "sporocysts")
sporo.big.forvelo


```

Sample 34 is definitely number 1
Sample 35 is definitely number 2
Sample 37 is definitely number 3
Sample 36 is definitely number 4

Here's lets save the filtered object for future use
```{r}
saveRDS(sporo.big.forvelo, file = "sporo.big.forvelo.rds") #saves this version of the dataset
sporo.big.forvelo <- readRDS(file = "/Users/ta13/R_git/velo_sporo/sporo.big.forvelo.rds")

```

If you want to remove the ZW genes....
```{r}
sporo.big.forvelo <- subset(sporo.big.forvelo, features = mygenesNoZW$genes)

```

```{r}
sporocysts3_neuro <- readRDS(file = "/Users/ta13/R_tutorials/sporocysts/sporocysts3_neuro.rds")
sporocysts3_neuro[["may.ident"]] <- Idents(object = sporocysts3_neuro)

DefaultAssay(sporocysts3_neuro) <- "RNA"
```

Extract list with metadata
```{r}
sporocysts3_neuro_metadata <- sporocysts3_neuro@meta.data

sporo.big.forvelo_metadata <- sporo.big.forvelo@meta.data
```

```{r}
library(tidyverse)
sporocysts3_neuro_metadata <- tibble::rownames_to_column(sporocysts3_neuro_metadata, "Cell.IDs")
sporo.big.forvelo_metadata <- tibble::rownames_to_column(sporo.big.forvelo_metadata, "Cell.IDs")

sporocysts3_neuro_metadata$Cell.IDs <- strtrim(sporocysts3_neuro_metadata$Cell.IDs, 32)

```


Combine metadat. I am going to do an inner join: only if cellID is in both metadata tables
```{r}
commonsmeta <- merge(sporocysts3_neuro_metadata, sporo.big.forvelo_metadata, by = "Cell.IDs")

commonsmeta$myIDs <- commonsmeta$Cell.IDs
commonsmeta$stage <- "sporocyst"
```



Here, I am going to make a new object with only cells in both seurat objects
```{r}
toRemove <-c(commonsmeta$Cell.IDs)

## filter them out:
commCells <- sporo.big.forvelo[,colnames(sporo.big.forvelo) %in% toRemove]

length(colnames(commCells))

commonsmeta <- commonsmeta %>%
     remove_rownames() %>%
     column_to_rownames(var = 'Cell.IDs')
```

Then i am going to update the metadata with the combined metadata
```{r}
commonsmeta$batch <- commonsmeta$myIDs


commonsmeta$batch <- strtrim(commonsmeta$batch, 15)
table(commonsmeta$batch)
commCells@meta.data <- commonsmeta
```

And now export of velocity analysis
```{r}
write.csv(x = commCells@meta.data, file = 'meta_filtered_fromOG_sporo_big_forvelo.csv')
write.csv(x = t(as.matrix(commCells@assays$sf@counts)), file = 'spliced_raw_filtered_fromOG_sporo_big_forvelo.csv')
write.csv(x = t(as.matrix(commCells@assays$uf@counts)), file = 'unspliced_raw_filtered_fromOG_sporo_big_forvelo.csv')
```

```{r}
saveRDS(commCells, file = "commCells_sporocysts.rds") #saves this version of the dataset
commCells <- readRDS(file = "/Users/ta13/R_git/velo_sporo/commCells_sporocysts.rds")

```

