---
title: "prep_all_mira_forscvelo"
author: "T Attenborough"
date: "11/01/2023"
output: html_document
---


```{r, message=FALSE}
library(remotes)
library(Seurat)
library(zeallot) # For %<-% that unpacks lists in the Python manner
library(DropletUtils)
library(tidyverse)
library(GGally) # For ggpairs
library(scales)
library(plotly)
library(BUSpaRse)
library(SeuratWrappers)
library(SeuratData)
library(SeuratDisk)
theme_set(theme_bw())
```

```{r}
mira.big.forvelo <- merge(commCells_sample1, y = c(commCells_sample2, commCells_sample3, commCells_sample4), add.cell.ids = c("Sample 1", "Sample 2", "Sample 3", "Sample 4"), project = "run1.combined")
mira.big.forvelo
```

Here's lets save the filtered object for future use
```{r}
saveRDS(mira.big.forvelo, file = "mira.big.forvelo.no.integrate.rds") #saves this version of the dataset
mira.big.forvelo <- readRDS(file = "/Users/ta13/R_git/mira_phate/mira.big.forvelo.no.integrate.rds")

```

If you want to remove the ZW genes....
```{r}
mira.big.forvelo <- subset(mira.big.forvelo, features = mygenesNoZW$genes)

```

```{r}
run1.combined <- readRDS(file = "/Users/ta13/R_git/filtered_v10_miracidia/run1.combined.v10_integrated_55.rds")

DefaultAssay(run1.combined) <- "RNA"
```

```{r}
DefaultAssay(run1.combined) <- "integrated"
run1.combined <- RenameIdents(object = run1.combined, 
                               "0" = "Muscle 1",
                               "1" = "Stem C",
                               "2" = "Stem D",
                               "3" = "Stem F",
                               "4" = "Stem A",
                               "5" = "Stem B",
                               "6" = "Neuron 1",
                               "7" = "Muscle 2",
                               "8" = "Neuron 2",
                               "9" = "Parenchyma 1",
                               "10" = "Stem E",
                               "11" = "Parenchyma 2",
                               "12" = "Protonephridia",
                               "13" = "Tegument",
                               "14" = "Neuron 3",
                               "15" = "Neuron 5",
                               "16" = "Stem G",
                               "17" = "Neuron 4", 
                              "18" = "Neuron 6")


run1.combined[["merge.ident"]] <- Idents(object = run1.combined)
run1.combined[["may.ident"]] <- Idents(object = run1.combined)
run1.combined[["temp.ident"]] <- Idents(object = run1.combined)

DimPlot(run1.combined, reduction = "umap", label=TRUE) #visulaises the UMAP
p2 <- DimPlot(run1.combined, reduction = "umap", label = TRUE, repel = TRUE)
p2

ggsave("run1.combined.v10_55PC_1res_lbl.pdf")
```

```{r}

run1.combined <- subset(run1.combined, features = mygenesNoZW$genes)

```

Extract list with metadata
```{r}
run1.combined_metadata <- run1.combined@meta.data

mira.big.forvelo_metadata <- mira.big.forvelo@meta.data
```

```{r}
library(tidyverse)
run1.combined_metadata <- tibble::rownames_to_column(run1.combined_metadata, "Cell.IDs")
mira.big.forvelo_metadata <- tibble::rownames_to_column(mira.big.forvelo_metadata, "Cell.IDs")

run1.combined_metadata$Cell.IDs <- strtrim(run1.combined_metadata$Cell.IDs, 24)

run1.combined_metadata$Cell.IDs <- str_to_title(run1.combined_metadata$Cell.IDs)
mira.big.forvelo_metadata$Cell.IDs <- str_to_title(mira.big.forvelo_metadata$Cell.IDs)

mira.big.forvelo_metadata$Cell.IDs <- str_replace_all(string=mira.big.forvelo_metadata$Cell.IDs, pattern=" ", repl="")
```

```{r}
#commonsmeta <- inner_join(run1.combined_metadata, mira.big.forvelo_metadata)
commonsmeta <- inner_join(run1.combined_metadata, mira.big.forvelo_metadata, by = "Cell.IDs")


```


Combine metadat. I am going to do an inner join: only if cellID is in both metadata tables
```{r}
commonsmeta <- merge(run1.combined_metadata, mira.big.forvelo_metadata, by = "Cell.IDs")
commonsmeta$stage <- "miracidia"
```

Then i am going to update the metadata with the combined metadata
```{r}
mira.big.forvelo@meta.data <- commonsmeta
```


And now export of velocity analysis
```{r}
write.csv(x = mira.big.forvelo@meta.data, file = 'meta_filtered_fromOG_mira_big_forvelo_v10_newlbls.csv')
write.csv(x = t(as.matrix(mira.big.forvelo@assays$sf@counts)), file = 'spliced_raw_filtered_fromOG_mira_big_forvelo_v10.csv')
write.csv(x = t(as.matrix(mira.big.forvelo@assays$uf@counts)), file = 'unspliced_raw_filtered_fromOG_mira_big_forvelo_v10.csv')
```


```{r}
table(mira.big.forvelo@meta.data$plex.x)
```



And now export of velocity analysis
```{r}
write.csv(x = mira.big.forvelo@meta.data, file = 'meta_filtered_fromOG_mira_big_forvelo_noZW.csv')
write.csv(x = t(as.matrix(mira.big.forvelo@assays$sf@counts)), file = 'spliced_raw_filtered_fromOG_mira_big_forvelo_noZW.csv')
write.csv(x = t(as.matrix(mira.big.forvelo@assays$uf@counts)), file = 'unspliced_raw_filtered_fromOG_mira_big_forvelo_noZW.csv')
```

Import also the sporo velo data
```{r}
sporo_veloCells <- readRDS(file = "/Users/ta13/R_git/velo_sporo/commCells_sporocysts.rds")
sporo_veloCells@meta.data$plex.x <- "sporo"
sporo_veloCells@meta.data$temp.ident <- sporo_veloCells@meta.data$may.ident

```

Just merge them?
```{r}
mira_and_sporo_velo <- merge(mira.big.forvelo, y = sporo_veloCells, add.cell.ids = c("mira_velo", "sporo_velo"), project = "mira_sporo")

```

```{r}
table(mira_and_sporo_velo@meta.data$plex.x)
table(mira_and_sporo_velo@meta.data$stage)
table(mira_and_sporo_velo@meta.data$temp.ident)
table(mira_and_sporo_velo@meta.data$may.ident)
table(mira_and_sporo_velo@meta.data$type.x)

```

And now export of velocity analysis
```{r}
write.csv(x = mira_and_sporo_velo@meta.data, file = 'meta_filtered_fromOG_mira_and_sporo.csv')
write.csv(x = t(as.matrix(mira_and_sporo_velo@assays$sf@counts)), file = 'spliced_raw_filtered_fromOG_mira_and_sporo.csv')
write.csv(x = t(as.matrix(mira_and_sporo_velo@assays$uf@counts)), file = 'unspliced_raw_filtered_fromOG_mira_and_sporo.csv')
```

Just merge them?
```{r}
mira_and_sporo_velo <- merge(mira.big.forvelo, y = sporo_veloCells, add.cell.ids = c("mira_velo", "sporo_velo"), project = "mira_sporo")

```


```{r}
justsample1 <- subset(x = mira_and_sporo_velo, subset = plex.x == "sample1")
justsample1mira_and_sporo_velo <- merge(justsample1, y = sporo_veloCells, add.cell.ids = c("mirasample1_velo", "sporo_velo"), project = "mirasample1_sporo")

```

And now export of velocity analysis
```{r}
write.csv(x = justsample1mira_and_sporo_velo@meta.data, file = 'meta_filtered_fromOG_justsample1mira_and_sporo_velo.csv')
write.csv(x = t(as.matrix(justsample1mira_and_sporo_velo@assays$sf@counts)), file = 'spliced_raw_filtered_fromOG_justsample1mira_and_sporo_velo.csv')
write.csv(x = t(as.matrix(justsample1mira_and_sporo_velo@assays$uf@counts)), file = 'unspliced_raw_filtered_fromOG_justsample1mira_and_sporo_velo.csv')
```

```{r}
table(justsample1mira_and_sporo_velo@meta.data$stage)
```

```{r}
justsample2 <- subset(x = mira_and_sporo_velo, subset = plex.x == "sample2")
justsample2mira_and_sporo_velo <- merge(justsample2, y = sporo_veloCells, add.cell.ids = c("mirasample2_velo", "sporo_velo"), project = "mirasample2_sporo")

```

And now export of velocity analysis
```{r}
write.csv(x = justsample2mira_and_sporo_velo@meta.data, file = 'meta_filtered_fromOG_justsample2mira_and_sporo_velo.csv')
write.csv(x = t(as.matrix(justsample2mira_and_sporo_velo@assays$sf@counts)), file = 'spliced_raw_filtered_fromOG_justsample2mira_and_sporo_velo.csv')
write.csv(x = t(as.matrix(justsample2mira_and_sporo_velo@assays$uf@counts)), file = 'unspliced_raw_filtered_fromOG_justsample2mira_and_sporo_velo.csv')
```

```{r}
table(justsample2mira_and_sporo_velo@meta.data$stage)
```

```{r}
justsample3 <- subset(x = mira_and_sporo_velo, subset = plex.x == "sample3")
justsample3mira_and_sporo_velo <- merge(justsample3, y = sporo_veloCells, add.cell.ids = c("mirasample3_velo", "sporo_velo"), project = "mirasample3_sporo")

```

And now export of velocity analysis
```{r}
write.csv(x = justsample3mira_and_sporo_velo@meta.data, file = 'meta_filtered_fromOG_justsample3mira_and_sporo_velo.csv')
write.csv(x = t(as.matrix(justsample3mira_and_sporo_velo@assays$sf@counts)), file = 'spliced_raw_filtered_fromOG_justsample3mira_and_sporo_velo.csv')
write.csv(x = t(as.matrix(justsample3mira_and_sporo_velo@assays$uf@counts)), file = 'unspliced_raw_filtered_fromOG_justsample3mira_and_sporo_velo.csv')
```

```{r}
table(justsample3mira_and_sporo_velo@meta.data$stage)
```


```{r}
justsample4 <- subset(x = mira_and_sporo_velo, subset = plex.x == "sample4")
justsample4mira_and_sporo_velo <- merge(justsample4, y = sporo_veloCells, add.cell.ids = c("mirasample4_velo", "sporo_velo"), project = "mirasample4_sporo")

```

And now export of velocity analysis
```{r}
write.csv(x = justsample4mira_and_sporo_velo@meta.data, file = 'meta_filtered_fromOG_justsample4mira_and_sporo_velo.csv')
write.csv(x = t(as.matrix(justsample4mira_and_sporo_velo@assays$sf@counts)), file = 'spliced_raw_filtered_fromOG_justsample4mira_and_sporo_velo.csv')
write.csv(x = t(as.matrix(justsample4mira_and_sporo_velo@assays$uf@counts)), file = 'unspliced_raw_filtered_fromOG_justsample4mira_and_sporo_velo.csv')
```

```{r}
table(justsample4mira_and_sporo_velo@meta.data$stage)
```

```{r}
table(justsample1@meta.data$p)
```

```{r}
justsample1 <- subset(x = mira_and_sporo_velo, plex.x == "sample1")

justsample4 <- subset(x = mira_and_sporo_velo, subset = plex.x == "sample4")

justsample41and4miravelo <- merge(justsample1, y = justsample4, add.cell.ids = c("mirasample1_velo", "mirasample4_velo"), project = "mirasample1and4")

```

And now export of velocity analysis
```{r}
write.csv(x = justsample41and4miravelo@meta.data, file = 'meta_filtered_fromOG_mirasample1and4_velo.csv')
write.csv(x = t(as.matrix(justsample41and4miravelo@assays$sf@counts)), file = 'spliced_raw_filtered_fromOG_mirasample1and4.csv')
write.csv(x = t(as.matrix(justsample41and4miravelo@assays$uf@counts)), file = 'unspliced_raw_filtered_fromOG_mirasample1and4.csv')
```